% !TEX program = xelatex
\documentclass[../../book.tex]{subfiles}
\begin{document}
\section{A}
\raggedcolumns
\begin{multicols}{2}
\begin{itemize}
\item[-] a (an)
\item[-] abandon
\\\emph{n.} abandonment
\\abandon oneself to sth/doing
\\{\color{violet}desert}
\item[-] ability
\item[-] able
\item[-] abnormal
\item[-] aboard \emph{adv./prep.}
\\{\color{violet}board a plane}
\item[-] about
\\was / were about to do sth when \mbox{-main} did
\item[-] above
\\\emph{opp.} below
\item[-] abroad
\\{\color{violet}broaden one{\textquoteright}s horizons}
\item[-] absence
\\absence of mind 心不在焉
\\ in the absence / presence of
\item[-] absent
\\\begin{tabular}{@{} r | @{\hspace{0.1em}} l @{}}
\multicolumn{1}{@{} r}{be} & absent from
\\& present at
\end{tabular}
\\absent-minded \emph{adj.}
\item[-] absolutely
\item[-] absorb
\\absorb A into B 把 A 并入 B
\\be absorbed in
\\\emph{n.} absorption
\\\emph{adj.} absorbing 引人入胜的
\item[-] abstract
\item[-] abuse
\item[-] academic
\\academic performance
\\academy \emph{n.} 研究所，学院
\item[-] accent
\\{\color{violet}dialect \emph{n.} 方言}
\item[-] accept
\\acceptance \emph{n.}
\\acceptable \emph{adj.}
\item[-] access
\\have access to sth
\\sth be accessible to sb
\\\phantom{sth be }{$\downarrow$\scriptsize 可达的；易懂的；平易近人的；可使用的}
\item[-] accident
\\by accident = accidentally
\item[-] accommadation
\\accommadate \emph{v.} \textcircled{1}给\ldots 提供膳宿\textcircled{2}容纳
\item[-] accompany
\\be accompanied by / with
\\keep sb company
\\in sb\textquoteright s company
\\in company with
\item[-] according to
= based on
\item[-] account
\\accountant
\\account for \textcircled{1}解释\textcircled{2}占比
\\give a vivid account of
\\take sth into account
\\an account of
\\on no account
\\open a bank account
\item[-] accurate
\\\emph{n.} accuracy
\item[-] accuse
\\accuse sb of = charge sb with
\item[-] ache
\\an aching leg
\item[-] achieve
\\accomplish / fulfill
\item[-] achivement
\\= accomplishment
\\a sense of $\sim$
\item[-] acid
\\acid rain
\item[-] acknowledge
\\-ment
\\$\sim$ doing
\\It is universally $\sim$ed that
\item[-] acquire
\\$\sim$ a good knowledge of
\\\emph{n.} acquisition
\item[-] across
\item[-] act
\\an act of kindness
\item[-] action
\\take action to do
\item[-] (in)active
\item[-] activity
\item[-] actor
\item[-] actress
\item[-] actually
\item[-] AD 公元
\\BC 公元前
\item[-] adapt
\\adapt oneself to 适应
\\be adapted for / from 改编
\\adaptable \emph{adj.}
\item[-] adaptation
\item[-] add
\\add A to B 把 A 加到 B
\\add to 增加，增添
\\add up to 合计
\\add up 把$\cdots$加起来
\\He added that\ldots
\\\emph{n.} addition in addition (to)
\\\emph{adv.} additionally
\item[-] addict （人）
\\be addicted to sth / doing
\\addictive \emph{adj.} 使人上瘾的
\item[-] addiction
\item[-] address
\\\emph{vt.} \textcircled{1}address sth 在$\cdots$上写收信人姓名地址 The letter was correctly addressed but was delivered to the wrong place.
\\\textcircled{2}address a meeting 在会议上发表演说
\\\textcircled{3}address a problem 解决
\\wrestle / cope with
\\handle / approach / fix
\\\textcircled{4}向$\cdots$说话 I was surprised that he addressed me in English.
\item[-] adjust
\\adjust (oneself) to
\\adjustable
\\\begin{tabular}{@{} r | @{\hspace{0.1em}} l @{}}
\multicolumn{1}{@{} r}{make} & an adjustment to
\\& adjustments
\end{tabular}
\item[-] administration
\item[-] admire
\\$\sim$ sb for sth
\\admirable
\\in admiration
\item[-] admit
\\admit doing 承认
\\admit sb to / into sp. 允许进入（录取，录用）
\\admission {\color{violet}permission submission}
\item[-] adopt
\\adoption
\item[-] adorable
\\adore doing
\\adoration
\\have an affection for
\item[-] adult
\\ripe \emph{adj.}（瓜果）\phantom{a}(im)mature$\rightarrow$maturity
\item[-] advance
\\\emph{vi.} \textcircled{1}游行示威\textcircled{2}前进，行进
\\\emph{vt.} \textcircled{1}发展，使进步\textcircled{2}促进，推动\textcircled{3}把$\cdots$提前
\\in advance
\\advance \emph{adj.} 先进的
\item[-] advantage
\\A have an advantage over B in C
\\(dis)advantageous \emph{adj.} 有利的，优势的\phantom{a}{\color{violet}courageous}
\item[-] adventure
\\adventurous
\item[-] advertise \emph{v.}
\\advertising \emph{n.} 广告业
\\advertiser \emph{n.} 广告者
\item[-] advertisement (ad)
\item[-] advice
\item[-] advise
\\\begin{tabular}{@{} r @{}}
$\sim$/suggest/recommend$\left\{
\begin{array}{@{}l@{}}
\text{that \mbox{-main} (should) do} \\
\text{doing}
\end{array}
\right.$
\end{tabular}
\\advise / recommend sb to do
\\suggest sb doing
\item[-] advocate
\\\emph{v.} advocate doing
\\\emph{n.} 提倡者，主张者 an $\sim$ of
\item[-] affair
\item[-] affect
\\be affected by 影响；打动，感染
\\be affected with 感染（疾病）
\\{\color{violet}have an affection for = have a fancy for}
\item[-] afford
\\afford to do
\\affordable
\\affordability
\item[-] afraid
\\be $\sim$ of / to do
\item[-] Africa
\item[-] African
\item[-] after
\item[-] afternoon
\item[-] afterward
\item[-] again
\item[-] against
\\\begin{tabular}{@{} r | @{\hspace{0.1em}} l @{}}
\multicolumn{1}{@{} r}{反对} & 支持
\\be against& for
\\& in favor of
\end{tabular}
\item[-] age
\\\emph{vi.} 变老，老年化 ageing society / process
\\at the age of
\\aged + 年龄：后置定语
\item[-] agency 代理商
\\ agent 代理人
\\travel agency
\item[-] agenda
\item[-] ago
\\I lived in China 3 years ago.
\\I had lived in China 3 years before.
\item[-] agree
\\agree with sb
\\agree on 就$\cdots$达成共识
\\agreeable
\item[-] agreement
\item[-] agriculture
\\agricultural
\item[-] ahead
\\ahead of time = in advance
\item[-] aid
\\first aid 急救
\item[-] aim
\\aim to do 目的做
\\be aimd at 旨在，针对$\cdots$
\\be intended / designed for sb / to do
\item[-] air
\item[-] airline
\item[-] airport
\item[-] alarm
\\alarmed alarming
\item[-] alcohol 酒精
\\alcoholic \emph{n.} 酗酒者 \emph{adj.} 含酒精的
\item[-] alive 仅表语
\\sth come alive 变活跃，热闹
\\living 活着的 live 现场直播的
\item[-] all
\item[-] allow
\\$\sim$ sb to do
\\allow for 考虑到，顾及到
\item[-] almost
\item[-] alone
\item[-] along
\item[-] alongside
\item[-] aloud
\item[-] already
\item[-] also
\item[-] alternative
\\\begin{tabular}{@{} r | @{\hspace{0.1em}} l @{}}
\multicolumn{1}{@{} r}{have no} & $\sim$ but to do
\\& option
\\& choice
\end{tabular}
\item[-] although
\item[-] altogether
\item[-] always
\item[-] a.m.
\item[-] amateur
\\\emph{opp.} professional
\item[-] amazing
\item[-] ambition
\item[-] ambitious
\item[-] ambulance
\item[-] America
\item[-] American
\item[-] among
\item[-] amount
\\{\small amount to = add up to = come to 总计}
\\{\small a large amount of = large amounts of [U]}
\item[-] amuse
\\amused amusing
\item[-] analyse (analyze)
\\analysis \emph{n.} give an analysis of
\item[-] ancestor
\item[-] ancient
\item[-] and
\item[-] anger
\item[-] angle 角 \phantom{a}{\color{violet}angel \emph{n.} 天使}
\item[-] angry
\item[-] animal
\item[-] ankle 脚踝
\item[-] announce
\\announcement
\\It is announced that\ldots
\item[-] annoy
\\annoyance annoyed annoying
\item[-] annual
\item[-] another
\item[-] answer
\\answer to a question
\\answer the door / telephone
\\anwser for\ldots 对$\cdots$承担后果
\item[-] ant
\item[-] anticipate
\\anticipation
\\It is anticipated that\ldots
\item[-] antique
\item[-] anxiety 焦虑；渴望
\item[-] anxious
\\be anxious $\underset{\text{\normalsize 渴望}}{\text{for}} / \underset{\text{\normalsize 担心}}{\text{ about}}$
\item[-] any
\item[-] anybody
\item[-] anyhow
\\{\color{violet}somehow \emph{adv.}\textcircled{1}不知怎么搞的，莫名其妙的\textcircled{2}以某种方式}
\item[-] anyone
\item[-] anything
\item[-] anyway
\item[-] anywhere
\item[-] apart
\\$\underset{\text{\normalsize (tore, torn)}}{\text{tear}}$ sth apart
\\take sth apart
\\set A apart from B 使 A 有别于 B，脱颖而出
\\= distinguish A from B
\item[-] apartment
\\flat
\item[-] apologise (apologize)
\\apology
\\apologise to sb for sth
\\owe / make an apology to sb for sth
\item[-] apparently
\\= obviously / clearly / evidently
\item[-] appeal
\\appeal to sb 吸引
\\appeal to sb to do / for sth 呼吁，恳求
\\apealing \emph{adj.}
\item[-] appear
\\= emerge
\\appearance
\\It appears / seems that
\item[-] appetite
\\have an appetite for
\item[-] applaud
\\thunderous applause come in waves
\item[-] apple
\item[-] applicant
\\apply to A for B 申请
\\apply A to B 应用
\\apply oneself to doing 致力于
\item[-] application
\item[-] apply
\item[-] appointment
\\appoint 约定，安排，任命，委任
\\make an appointment with sb
\\appoint + 地 / 时
\\the appointed place / time
\item[-] appreciate
\\\textcircled{1}欣赏，赏识，重视
\\\textcircled{2}感激 $\sim$ to doing
\\\phantom{\textcircled{2}感激 }I would $\sim$ it if you could\ldots
\\\textcircled{3}领会，理解，意识到
\\be appreciative of 感激
\\appreciation
\item[-] approach
\\\emph{n.}\textcircled{1}通道，入口\textcircled{2}方法，方式 $\sim$ to doing%
\textcircled{3}逼近，即将到来 with the $\sim$ of
\\\emph{v.}\textcircled{1}接近\textcircled{2}解决 $\sim$ a problem
\item[-] (in)appropriate
\\be $\sim$ for / to
\item[-] approve \emph{vt.} 批准，通过
\\(dis)approve of 赞成
\\(dis)approval \emph{n.}
\item[-] April
\item[-] arch
\item[-] architect
\\architecture
\item[-] area
\item[-] argue
\\\textcircled{1}争吵
\\\textcircled{2}说服 \begin{tabular}{@{} r | @{\hspace{0.1em}} l @{} | @{\hspace{0.1em}} l @{}}
\multicolumn{1}{@{} r}{} & \multicolumn{1}{@{\hspace{0.1em}} l}{$\sim$\phantom{a} sb} & into \phantom{a} doing
\\& talk & out of
\end{tabular}
\\argument
\item[-] arise (arose, arisen) 出现，发生
\\{\small A arise / result from B = B result in A B 导致 A}
\item[-] arm
\\be armed / equipped with
\item[-] army
\item[-] around
\item[-] arrangement
\\make an arrangement for
\\arrange for sb to do sth
\\arrange sth for sb
\item[-] arrest
\item[-] arrive at / in
\\arrival
\item[-] arrow
\item[-] art
\\artistic
\item[-] article
\item[-] artist
\item[-] as
\item[-] ashamed
\\be ashamed of
\\shameful \emph{adj.} 令人羞耻的
\item[-] Asia
\item[-] Asian
\item[-] aside
\\set / lay / put aside
\\\textcircled{1}把$\cdots$放一边置之不理%
\\\textcircled{2}存钱，储蓄
\\set aside some time to do sth
\item[-] ask
\\ask sb for sth
\item[-] asleep 仅表语
\item[-] aspect
\\in all aspects
\item[-] assess
\\assessment self-assessment
\item[-] assign 分配，布置，指派，确定时间地点
\\assignment \emph{n.} 作业
\item[-] assistant
\item[-] association 协会；联系
\\associate with sb 和$\cdots$打交道
\\be associated with 和$\cdots$有关联
\item[-] assume
\\\textcircled{1} 认为，猜想
\\\textcircled{2} 承担（责任） $\sim$ responsibility for
\\\textcircled{3} 就职 $\sim$ office
\\$\underset{\text{\emph{conj.}}}{\text{Assuming}}$ that\ldots 倘若，假使
\item[-] assumption
\item[-] astonish
\item[-] astronaut
\item[-] astronomer
\\astronomy
\item[-] at
\item[-] athelete
\\athletic 强壮的，爱运动的
\item[-] Atlantic
\item[-] atmosphere
\item[-] attach
\\attach A to B 固定，贴，附
\\be attached to \textcircled{1}依恋，爱恋\textcircled{2}附属于\textcircled{3}有关联
\\attachment
\item[-] attack
\item[-] attain
\item[-] attempt
\\$\sim$ to do
\\in an attempt tp do 试图，企图，尝试
\item[-] attend
\\\textcircled{1}出席，参加
\\\textcircled{2}照料，处理（$\sim$ to）
\\\textcircled{3}上学
\begin{tabular}{@{} r | @{\hspace{0.1em}} l @{}}
\multicolumn{1}{@{} r}{$\sim$} & class
\\& school
\\& university
\end{tabular}
\\attendance
\item[-] attention
\\pay attention to
\\fix / concentrate / focus one\textquoteright s $\sim$ on
\item[-] attitude to / towards
\item[-] attract
\\attractive attraction
\item[-] audience
\item[-] August
\item[-] aunt
\item[-] Australia
\item[-] Australian
\item[-] author
\item[-] authority
\item[-] automatic
\item[-] autonomous
\item[-] autumn
\item[-] available
\\be $\sim$ to
\\availability
\item[-] average 平均的，普通的
\\on $\sim$
\item[-] avoid
\\$\sim$ doing
\\avoidance avoidable
\item[-] awake (awoke, awoken)
\\\emph{vt.} 唤起，唤醒 wake up
\\\emph{adj.} [表]醒着的
\item[-] award
\\\emph{n.} 奖
\\\emph{vt.} 颁发，授予
\item[-] aware
\\be $\sim$ of
\\arouse one\textquoteright s awareness of
\item[-] away
\item[-] awesome
\item[-] awful
\item[-] awkward 笨拙的；尴尬的
\item[-] abolish
\item[-] absurd
\\ridiculous
\item[-] abundant
\\be $\sim$ in = abound in
\item[-] abrupt
\item[-] accelerate
\\speed up
\item[-] accomplish
\item[-] accumulate
\item[-] acute
\item[-] accustomed
\\be $\sim$ to doing
\item[-] acquaintance
\\make one\textquoteright s $\sim$ / make the $\sim$ of sb
\item[-] adolescence 青春期，青春
\item[-] adolescent 青少年；青春期的
\item[-] adequate
\\\textcircled{1} 胜任
\\\begin{tabular}{@{} r | @{\hspace{0.1em}} l @{}}
\multicolumn{1}{@{} r}{be} & $\sim$ \phantom{a} to doing
\\& equal
\\& up
\end{tabular}
\\be qualified for / to do
\\\textcircled{2} 足够的 be $\sim$ for
\item[-] aggressive
\item[-] allergic be $\sim$ to
\item[-] alley
\item[-] allocate
\item[-] allowance
\item[-] alphabet
\item[-] altitude
\item[-] ambassador
\item[-] ambassadress
\item[-] anchor \emph{n.} 锚 \emph{vi.} 停泊，泊船
\item[-] anecdote
\item[-] anniversary
\item[-] Antarctic 南极，南极地区
\\Antarctica 南极洲
\item[-] approximately = roughly
\item[-] apron
\item[-] arbitary
\item[-] ample sufficient
\item[-] Arctic 北极
\item[-] arithmetic 算术
\\algebra 代数 geometry 几何
\item[-] atom
\item[-] authentic
\item[-] avenue
\item[-] AI (artificial intelligence)
\item[-] alert
\item[-] app
\end{itemize}
\end{multicols}
\end{document}