% !TEX program = xelatex
\documentclass[../../book.tex]{subfiles}
\begin{document}
\section{B}
\raggedcolumns
\begin{multicols}{2}
\begin{itemize}
\item[-] baby
\item[-] back \emph{v.} 支持，支援，支柱
\\back off 离开，后退
\item[-] background
\item[-] backward
\item[-] bacon
\item[-] bad
\\be bad / good for
\\be harmful / beneficial to
\\do harm to
\item[-] badminton
\item[-] bag
\item[-] bakery
\\bake \emph{v.} baker \emph{n.}
\item[-] balance
\\balanced
\item[-] ball
\item[-] ballet
\item[-] balloon
\\\emph{n.} 气球
\\\emph{v.} 膨胀，肿胀，激增
\item[-] bamboo
\item[-] ban (banned)
\\ban sb from doing
\\put a ban on
\item[-] banana
\item[-] band
\item[-] bank
\item[-] bar
\item[-] barbeque
\item[-] barely
\item[-] bark
\item[-] barrier
\item[-] base
\\base A on B
\\A be based on B
\\based on
\item[-] baseball
\item[-] basic
\\basically
\item[-] basin
\item[-] basis
\\on the basis of
\item[-] basket
\item[-] basketball
\item[-] bat 拍；蝙蝠
\item[-] bath
\\\emph{n.} take a bath
\\bathe \emph{v.} be bathed in
\item[-] bathroom
\item[-] battery
\item[-] battle
\item[-] bay
\item[-] BC
\item[-] be (am, are, is)
\item[-] beach
\item[-] bean
\item[-] bean curd (tofu)
\item[-] bear
\\\emph{n.} give sb a bear hug
\\\emph{v.}(bore, borne / born*)
\\\textcircled{1} 忍受，容忍 
\\\begin{tabular}{@{} c @{\hspace{0.1em}} l @{}}
bear & doing
\\stand &
\\tolerate &
\\put up with &
\end{tabular}
\\\textcircled{2} 经受得住 The ice can\textquoteright t bear your weight.
\\\textcircled{3} 携带
\\\textcircled{4} 结果实，生育*（过去分词 born 仅用于出生）He was born yesterday.
\item[-] beard
\item[-] beat (beat, beaten)
\\\textcircled{1} defeat
\\\textcircled{2} 心脏/脉搏的跳动
\\\textcircled{3} 有规律地击打 beat a drum
\\The rain beat against the windows.
\item[-] beautiful
\\beautify \emph{vt.} 美化
\\{\color{violet}purify \emph{vt.} 纯化 simplify \emph{vt.} 简化}
\item[-] beauty
\item[-] because
\item[-] become (became, become)
\item[-] bed
\item[-] bedroom
\item[-] beef
\item[-] beer
\item[-] before
\item[-] begin (began, begun)
\item[-] behalf
\\on behalf of / on one\textquoteright s behalf
\\representing\ldots
\item[-] behave
\\behave oneself
\\well-behaved
\item[-] behaviour (behavior)
\item[-] behind
\item[-] being
\\well-being human-being(s)
\item[-] belief
\\I have a firm belief that\ldots
\item[-] believe
\\believe in
\item[-] bell
\item[-] belong
\\A belong to B
\\belongings \emph{n.}
\\a sense of belonging
\item[-] below
\item[-] belt
\\safety belt \phantom{a} fasten your safety belt
\item[-] bend (bent, bent)
\\bend over
\\bend oneself to sth / doing 专心于
\item[-] beneath
\item[-] benefit
\\\begin{tabular}{@{} r | @{\hspace{0.1em}} l @{}}
\multicolumn{1}{@{} r}{be} & beneficial to
\\& of benefit
\end{tabular}
\item[-] beside
\\next to
\item[-] besides
\item[-] best
\\make the best of
\item[-] bet
\\I can bet.
\item[-] better
\item[-] between
\item[-] beyond
\\beyond words / imagination / $\cdots$
\item[-] big
\item[-] bike (bicycle)
\item[-] bill \emph{n.} 账单，纸币，钞票，清单
\item[-] billion
\item[-] biology
\\biologist biological
\item[-] bird
\item[-] birth
\\bear
\\give birth to
\item[-] birthday
\item[-] biscuit
\item[-] bit
\\a bit (of) water
\item[-] bite (bit, bitten)
\\take a bite of {\color{violet}have a taste of}
\item[-] bitter
\item[-] black
\item[-] blackboard
\item[-] blame
\\\textcircled{1}blame sth on sb 归咎于
\\\phantom{\textcircled{1}}owe sth to sb 归功于
\\\textcircled{2}be to blame for 责备
\\\textcircled{3}be to blame for 理应受责备
\\\textcircled{4}take the blame for
\item[-] blank
\\go blank
\item[-] balnket
\item[-] bleed (bled, bled) bleeding
\item[-] bless
\\God bless us.
\\blessing \emph{n.} 祝福，恩宠，幸事
\item[-] blind
\\turn a blind eye to
\\turn a deaf ear to
\item[-] block
\\\emph{v.} 阻挡，阻塞，封锁 a blocked nose
\\\emph{n.} 木块；街区；大厦，大楼；障碍
\item[-] blog
\item[-] blood
\item[-] blouse
\item[-] blow
\\blow up a balloon 吹饱$\rightarrow$爆炸
\\blow out a candle
\\be a blow to 对$\cdots$是一个沉重打击
\item[-] blue \emph{adj.} 忧郁的，沮丧的
\item[-] board
\item[-] boat
\\by boat
\item[-] body
\item[-] boil
\item[-] bomb
\\The bomb exploded.
\item[-] bond
\\form a bond with
\\strengthen the $\sim$ between A and B
\item[-] bone \phantom{a} bony
\item[-] bonus
\item[-] book
\item[-] boost
\item[-] boot
\item[-] border
\item[-] bored
\\bore \emph{vt.} boredom \emph{n.}
\\be bored with
\\be tired of
\\be fed up with
\item[-] boring
\item[-] born
\item[-] borrow
\item[-] boss
\item[-] botanical \phantom{a} botany botanist
\item[-] both
\\not \ldots{} all/both/every/\ldots 部分否定
\item[-] bother
\\bother sb
\\\begin{tabular}{@{} r | @{\hspace{0.1em}} l @{}}
\multicolumn{1}{@{} r}{Don\textquoteright t bother} & to do
\\& doing
\end{tabular}
\item[-] bottle
\item[-] bottom
\item[-] bounce
\\bounce a basketball
\item[-] bound
\\be bound to do
\item[-] boundary
\item[-] bow
\\bow to sb
\item[-] bowl
\item[-] bowling
\item[-] box
\item[-] boxing
\item[-] boy
\item[-] brain
\item[-] branch 树枝；分支；子公司；分店
\\tree branches
\item[-] brave
\\bravery
\\{\color{violet}courage courageous}
\item[-] bread
\item[-] break
\item[-] breakfast
\item[-] breast
\item[-] breath
\\breathless 气喘吁吁的；呼吸急促的
\\take a deep breath
\\hold one\textquoteright s breath
\\out of breath, \ldots
\item[-] breathe
\\breathe a sigh of relief
\\breathe in / out
\item[-] brick
\item[-] bride / bridegroom
\\bridal \emph{adj.} 新娘的，婚礼的
\item[-] bridge
\\bridge the gap between A and B
\item[-] brief
\\In brief / To be brief / Briefly speaking, \ldots
\\brief sb about sth 简单介绍
\item[-] bright
\\brighten my day / future
\item[-] brilliant
\item[-] bring (brought, brought)
\item[-] Britain
\item[-] British
\item[-] broad \phantom{a} broaden
\item[-] broadcast ($\sim$ed/$\sim$, $\sim$ed/$\sim$)
\\\emph{n.} 电视节目，广播节目
\\\emph{v.} 广播，播送，传播信息 The concert will be $\sim$ed live.
\item[-] brochure
\item[-] brother
\item[-] brown
\item[-] brush
\item[-] budget
\\on a tight budget
\item[-] buffet
\item[-] build
\item[-] building
\item[-] bunch 串，束，扎
\\a bunch of keys / flowers
\item[-] burn
\\have a burning desire to do
\\with a buring desire
\item[-] bury
\\bury oneself in
\\be buried in
\item[-] bus
\item[-] business 生意；公司；事情
\\It\textquoteright s none of your business.
\item[-] busy
\\busy / occupy onnself in doing / with sth
\\be busy / occupied
\item[-] but
\item[-] butcher
\item[-] butter
\item[-] button
\\\emph{n.} 按钮；纽扣
\\\emph{v.} 系纽扣，扣住 Please button your coat.
\item[-] buy (bought, bought)
\\purchase \phantom{a} make a purchase
\item[-] by
\item[-] bachelor
\item[-] bacterium (\emph{pl.} bacteria)
\item[-] baggage \phantom{a} luggage
\item[-] balcony
\item[-] bandage
\item[-] barber \phantom{a} barbershop
\item[-] bargain
\\\emph{vi.} $\sim$ with sb about sth
\\\emph{n.} 便宜货
\item[-] basement
\item[-] beg \phantom{a} beggar
\item[-] belly
\item[-] bench
\item[-] betray 背叛；泄露
\item[-] bid (bid, bid)
\\\textcircled{1}出价格\textcircled{2}投标\textcircled{3}命令，吩咐
\\\textcircled{4}\begin{tabular}{@{} r | @{\hspace{0.1em}} l @{}}
\multicolumn{1}{@{} r}{bid} & goodbye \phantom{aaa} to sb
\\& good night / moring
\end{tabular}
\item[-] biography
\item[-] booth \phantom{a} stand
\item[-] boycott \emph{v.} 抵制，拒绝参加
\item[-] brake \emph{v./n.} 刹车；车闸
\item[-] brand \emph{n.} 品牌，商标，牌子
\\brand-new \emph{adj.} 崭新的
\item[-] broom
\item[-] brewary
\item[-] bungalow
\item[-] breakthrough
\\make a (huge) $\sim$ in
\item[-] burden \emph{vt.} 使有负担 / 重担
\\be burdened with
\item[-] burglar 盗贼
\\thief 小偷
\item[-] butterfly
\item[-] burst (burst, burst)
\\\emph{vt./vi.} { \small
\\\textcircled{1}爆裂，破裂，胀开
\\ My stomach will $\sim$.
\\ The balloon will $\sim$ if you blow it up any more.
\\ The dam $\sim$ under the weight of water.
\\ He felt he would $\sim$ with anger and shame.
\\\textcircled{2}闯入，破门而入 burst/break into sp
\\\textcircled{3}突然$\cdots$ 
\begin{tabular}{@{} r | @{\hspace{0.1em}} l @{}}
\multicolumn{1}{@{} r}{burst} & into sth
\\& out doing
\end{tabular}
\\\textcircled{4}充满着
\\be bursting with passion/enthusiasm/\ldots
\\The road is $\sim$ing with cars.
\\\emph{n.} \textcircled{1}裂口，爆裂
\\\textcircled{2}（感情）迸发，（事情）突发
\\a burst of passion/\ldots
}
\item[-] bee
\item[-] bias
\item[-] bin
\item[-] bug
\item[-] bully
\end{itemize}
\end{multicols}
\end{document}