% !TEX program = xelatex
\documentclass[../../book.tex]{subfiles}
\begin{document}
\section{C}
\raggedcolumns
\begin{multicols}{2}
\begin{itemize}
\item[-] cabbage
\item[-] caf\'e
\item[-] cafeteria
\item[-] cage
\\a caged bird
\item[-] cake
\item[-] calculate
\\calculator calculation
\item[-] calendar
\item[-] call
\item[-] calligraphy
\\calligrapher
\item[-] calm
\\\emph{v.} calm down 使冷静 \phantom{a} calmness
\\\emph{adj.}\textcircled{1}（人）沉着冷静的\textcircled{2}（湖）风平浪静的
\item[-] calorie
\item[-] camel
\item[-] camera
\item[-] camp
\\summer camping
\item[-] campaign
\item[-] campus
\item[-] can
\\a canned food
\\a garbage can / bin 垃圾桶 / 箱
\item[-] Canada
\item[-] Canadian
\item[-] canal
\item[-] cancel
\item[-] cancer
\item[-] candidate
\\a candidate for
\\I am a $\sim$ for the position.
\item[-] candle
\\blow out a $\sim$
\\light a $\sim$
\item[-] candy \phantom{a} sweet
\item[-] canteen
\item[-] cap
\item[-] capable
\\be capable of doing
\\\emph{n.} capability \emph{adv.} capably
\item[-] capacity
\item[-] capital \emph{n.} 首都；大写字母；资本，资金
\item[-] capsule \emph{n.} 胶囊；太空舱
\item[-] captain
\item[-] car
\item[-] carbon
\\lead a low-carbon life
\item[-] card
\item[-] care \phantom{a} careful careless
\item[-] career
\item[-] carpet
\item[-] carrot
\item[-] carry
\\\emph{v.} \textcircled{1} 运，扛，搬
\\\textcircled{2} 肩负 carry responsibility
\item[-] cartoon
\item[-] carve
\item[-] case
\\in case {\scriptsize 以防万一（后用一般现在时表示一般将来时）}
\item[-] cash
\item[-] cast \emph{n.} 演员阵容
\\\begin{tabular}{@{} r | @{\hspace{0.1em}} l @{}}
cast & a shadow on
\\& doubt on
\\& light on
\end{tabular}
\item[-] castle
\item[-] cat
\item[-] catch
\\catch one\textquoteright s eye $\rightarrow$ eye-catching
\\catch sight of
\item[-] category
\item[-] cattle [\emph{pl.}]
\item[-] cause
\\\emph{n.} 原因 $\sim$ of \phantom{a} reason for
\\\emph{v.} 导致 $\sim$ sb to do
\item[-] cave
\item[-] cease \phantom{a} quit
\item[-] ceiling \emph{n.} 天花板；上限 \phantom{} {\color{violet}ground 下限}
\item[-] celebrate
\\\begin{tabular}{@{} r | @{\hspace{0.1em}} l @{}}
\multicolumn{1}{@{} r}{be celebrated} & for 因$\cdots$出名
\\& as 作为
\end{tabular}
\item[-] celebrity
\item[-] cell
\item[-] cent
\item[-] centimetre (centimeter)
\item[-] central
\item[-] centre (center)
\item[-] century
\item[-] certain \emph{n.} (un)certainty
\\\textcircled{1} 有把握的，确定的，肯定的
\\\textcircled{2} 某个，某些
\\a $\sim$ student = some student
\\certain students
\item[-] certainly
\item[-] certificate 证明，证书，文凭
\item[-] chain
\\\emph{n.} a chain store / reacting
\\\emph{v.} 用锁链拴住 a chained dog
\item[-] chair
\\\emph{n.} 椅子 sink into a chair
\\\emph{v.} 主持 chair a meeting
\item[-] chairman / chairwoman
\item[-] chalk
\item[-] challenge
\\\begin{tabular}{@{} r @{}!{\color{violet}\vrule} l @{}}
\multicolumn{1}{@{} r}{rise to} & $\sim$s 迎接挑战
\\& {\color{violet}fame}
\\& {\color{violet}one\textquoteright s feet}
\end{tabular}
\item[-] champion
\item[-] chance
\\by chance
\item[-] change
\\changeable
\item[-] channel 频道，水渠，渠道
\item[-] chaos
\\in chaos = out of order
\\in order
\\(be) in a mess = messy
\item[-] chapter
\item[-] character
\\\emph{n.} \textcircled{1} 人物角色
\\\textcircled{2} 特点，特征（笼统的）
\\\textcircled{3} 性格 \textcircled{4} 字体
\item[-] characteristc
\\\emph{n.} 特点，特征（具体的）
\\ {\color{violet}technology technique}
\\\emph{adj.} 典型的 = typical
\\It is $\sim$ of sb to do\ldots
\item[-] charge
\\\emph{v.} \textcircled{1}$\sim$ sb -money for 征收
\\\textcircled{2}充电 My battery needs charging.
\\\textcircled{3}控告 $\sim$ sb with = accuse sb of
\\\textcircled{4}猛冲 charge into = storm into
\\\emph{n.} in charge of
\\in the charge of = in one\textquoteright s charge
\\take charge of
\\be free of charge 免费
\\{\color{violet}in control / pessession of\\in the $\sim$ of}
\item[-] charity
\item[-] chart
\item[-] chat
\item[-] cheap
\item[-] cheat
\item[-] check
\item[-] cheek
\item[-] cheer
\\cheer up
\\cheer on
\\cheerful
\item[-] cheese
\item[-] chef
\item[-] chemical
\item[-] chemist
\item[-] chemistry
\item[-] chess
\item[-] chest
\item[-] chew
\item[-] chicken
\item[-] chief 首要的，主要的，首席的
\item[-] child (\emph{pl.} children)
\item[-] China
\item[-] china
\item[-] Chinese
\item[-] chocolate
\item[-] choice
\\have no $\sim$ but to do
\item[-] choke 使窒息；卡住，说不出话
\item[-] choose (chose, chosen)
\item[-] chopsticks
\\disposable $\sim$ 一次性筷子
\item[-] chorus
\\\emph{n.} 合唱团；异口同声
\\\emph{vi.} 齐唱；异口同声地说
\item[-] Christmas
\\on $\sim$ Eve
\item[-] church
\item[-] cigarette
\item[-] cinema
\item[-] circle
\item[-] circuit
\item[-] circumstance
\\\begin{tabular}{@{} r | @{\hspace{0.1em}} l @{}}
\multicolumn{1}{@{} r}{in / under} & the $\sim$s
\\& no {\color{violet}$\rightarrow\left\{
\begin{array}{@{}l@{}}
\text{at no time}
\\\text{by no means}
\\\text{in no way}
\\\text{on no account}
\\\text{$\cdots$}
\end{array}
\right.$}
\end{tabular}
\item[-] circus 马戏团
\item[-] cite
\item[-] citizen 市民 \phantom{a} {\color{violet}resident 居民}
\item[-] city
\item[-] civil
\\\emph{adj.} \textcircled{1} 文明有礼的
\\\textcircled{2} 国内的 a $\sim$ war
\\\textcircled{3} 公民的 $\sim$ right
\item[-] civilian 平民
\item[-] civilisation (civilization)
\\civilise \emph{vt.}
\\civilised
\item[-] claim
\\\emph{vt./n.}\textcircled{1}声称，主张\textcircled{2}剥夺（生命）
\\\textcircled{3}认领\textcircled{4}索取
\item[-] clap
\item[-] clarify \emph{vt.}
\\\emph{n.} clarity
\\{\color{violet}application\\qualification\\classification\\satisfaction}
\item[-] class \textcircled{1}班级\textcircled{2}等级 first-class
\item[-] classic
\item[-] classmate
\item[-] classroom
\item[-] clay
\item[-] clean
\item[-] clear \emph{vi.}（天）放晴，晴朗
\item[-] clerk 职员
\item[-] clever
\item[-] click
\item[-] client
\item[-] climate
\item[-] climb 上涨
\item[-] clinic \phantom{a}{\color{violet}panicked picnicked}
\item[-] clock
\\around the clock 不停息的，全天候的
\item[-] clone
\item[-] close
\\be close to / approaching
\\He is $\sim$ to 40 years.
\item[-] cloth
\item[-] clothes
\item[-] cloud
\item[-] cloudy
\item[-] club
\item[-] clue 线索，提示
\item[-] coach \emph{n. / v.}
\item[-] coal
\item[-] coast
\item[-] coat
\item[-] coffee
\item[-] coin
\item[-] cold
\item[-] collapse 倒塌，瓦解，崩溃
\item[-] collar 领子 turn up the collar 翻起
\item[-] collect
\item[-] collection
\item[-] college
\item[-] colour (color) \phantom{a} colorful
\item[-] column
\item[-] combine \phantom{a} $\sim$ A with / and B
\item[-] come
\item[-] comedy \phantom{a} comedian 喜剧演员
\item[-] comfort
\item[-] comfortable
\\uncomfortable discomfort misfortune
\item[-] comic 戏剧的，滑稽的
\item[-] comment
\\comment on
\\make $\sim$s on
\item[-] commercial
\\\emph{n.} 电视广告
\\\emph{adj.} 商业的 commerce \emph{n.}
\item[-] commit
\\\emph{v.}\textcircled{1}犯 $\sim$ a crime/mistake/murder
\\\textcircled{2}投入 $\sim$ -time to doing / sth
\\\textcircled{3} \begin{tabular}{@{} r | @{\hspace{0.1em}} l @{}}
\multicolumn{1}{@{} r}{} & commit \phantom{aaa} oneself to doing
\\& dedicate / devote / apply
\end{tabular}
\\committed \emph{adj.} 投入的
\item[-] commitment
\\\begin{tabular}{@{} r | @{\hspace{0.1em}} l @{}}
\multicolumn{1}{@{} r}{make a} $\sim$ to & doing
\\保证，承诺 & do
\\& sb
\end{tabular}
\item[-] committee
\item[-] common
\\A have sth in common with B
\item[-] communicate
\item[-] communication
\item[-] communist 共产主义者 \phantom{a} communism
\\{\color{violet}socialist socialism}
\item[-] community
\item[-] company
\\accompany \emph{v.} companion \emph{n.}
\item[-] compare
\\\begin{tabular}{@{} r | @{\hspace{0.1em}} l @{\hspace{0.4em}} l @{}}
\multicolumn{1}{@{} r}{$\sim$ A} & with B & 比较 be $\sim$ed with
\\& to & 比作
\end{tabular}
\item[-] comparison \phantom{a} by $\sim$
\item[-] compete
\item[-] competence
\\competent competitor competitive
\item[-] competition
\item[-] complain
\\complaint
\\complain to sb about sth
\item[-] complete
\\\emph{v.} 完成，竣工 \emph{adj.} 完整的
\\completely
\item[-] complex \phantom{a} complexity
\item[-] complicated \phantom{a} complicate \emph{vt.} 使复杂
\item[-] component
\item[-] compose
\\\textcircled{1} 创作，作曲
\\\textcircled{2} 组成
\begin{tabular}{@{} r | @{\hspace{0.1em}} l @{}}
\multicolumn{1}{@{} r}{be} & composed of
\\& made up of
\\\multicolumn{2}{@{} l}{consist of}
\end{tabular}
\item[-] composition \emph{n.} 作曲，作文；成分，构成
\item[-] comprehension \phantom{a} comprehend \emph{v.} 理解
\item[-] comprehensive
\\\emph{adj.} \textcircled{1} 有理解力的
\\\textcircled{2} 全面的，综合性的 well-rounded
\item[-] comprise
\item[-] computer
\item[-] concentrate \phantom{a} concentrated
\item[-] concept
\item[-] concern
\\\emph{n.} 担心，关心，忧虑 show $\sim$ for
\\\emph{v.}\textcircled{1}使担忧\textcircled{2}关系到，涉及到
\\\begin{tabular}{@{} r | @{\hspace{0.1em}} l @{}}
\multicolumn{1}{@{} r}{be concerned} & about 关心
\\& with 有关系
\end{tabular}
\\concerning \emph{prep.} = regarding
\\As far as sb/sth be concerned, \ldots
\item[-] concert
\item[-] conclude
\\What can be concluded is that\ldots
\\It can be concluded from \ldots{} that
\item[-] conclusion
\\I draw a conclusion that\ldots
\item[-] concrete \emph{n.} 混凝土 \emph{adj.} 具体的
\item[-] condition
\\(un)conditional
\\in good condition / shape
\\on condition that（条件状语从句，一般现在时表示将来时）条件是
\item[-] conduct
\\\textcircled{1} 指挥 conduct a bank
\\\textcircled{2} 做，干，执行，实施 
\begin{tabular}{@{} r | @{\hspace{0.1em}} l @{\hspace{0.2em}} | @{\hspace{0.1em}} l @{}}
\multicolumn{1}{@{} r}{} & \multicolumn{1}{@{\hspace{0.1em}} l @{}}{$\sim$ \phantom{a} an} & investigation on
\\& perform & operation
\end{tabular}
\\conductor 指挥；售票员
\item[-] conference
\item[-] confidence
\item[-] confirm \phantom{a} confirmation
\item[-] conflict
\item[-] Confucianism
\item[-] Confucius
\item[-] confused \phantom{a} confusion
\item[-] congratulation
\\\begin{tabular}{@{} l | @{\hspace{0.1em}} l @{}}
\multicolumn{1}{@{} r}{congratulations to sb} & on doing
\\congratulate sb &
\\celebrate sth &
\end{tabular}
\item[-] connect
\\\begin{tabular}{@{} r | @{\hspace{0.1em}} l @{}}
\multicolumn{1}{@{} r}{be connected} & with 和
\\& to 到
\end{tabular}
\item[-] consequence
\\As a consequence / result (of\ldots), \ldots 
\item[-] conservation \phantom{a} conserve \emph{v.}
\item[-] consider
\\consider doing
\\consider sb/sth (to be) + \emph{adj./n.}
\\take sth into consideration / account
\\have a considerable effect on
\\a considerable number of
\\considerate
\item[-] consist
\\consist $\left\{
\begin{array}{@{}l@{}}
\text{with 相符合，一致} \\
\text{of 由$\cdots$组成} \\
\text{in 在于 = lie in}
\end{array}
\right.$
\item[-] consistent
\\be consistent / correspond with 一致
\\consistency 始终如一，连贯
\item[-] constant
\item[-] constitution
\item[-] construction
\item[-] consultant
\item[-] consultation
\\consult sb about 咨询，请教
\\\mbox{consult with sb about : negotiate with sb}
\item[-] consume
\item[-] consumption
\item[-] contact
\\\emph{v.} contact sb
\\\emph{n.}
\item[-] contain
\\\begin{tabular}{@{} r @{} | @{\hspace{0.1em}} l @{}}
\multicolumn{1}{@{} r @{}}{} & contain my excitement 抑制
\\& restrain
\\& fight back my tears
\end{tabular}
\item[-] contemporary
\item[-] content
\\\emph{n.} 目录，内容
\\\emph{vt.}使满足 $\sim$ oneself with \phantom{} be $\sim$ed with
\\\emph{adj.} 满足的 = satisfied \phantom{a} be $\sim$ with
\item[-] contest \phantom{a} contestant 参赛选手
\item[-] context 上下文，语境，背景
\item[-] continent
\item[-] continue
\\continuation continuous
\item[-] contract
\\\begin{tabular}{@{} r @{} | @{\hspace{0.1em}} l @{}}
\multicolumn{1}{@{} r @{}}{} & sign \phantom{a} a $\sim$
\\& negotiate
\end{tabular}
\\contraction \emph{n.} 缩小
\item[-] contradictory
\\A contradict B
\\contradiction
\item[-] contrary
\\on the contrary, \ldots
\\A be contrary to B
\item[-] contrast
\\by contrast / comparison
\item[-] contribution
\\\begin{tabular}{@{} r | @{\hspace{0.1em}} l @{}}
\multicolumn{1}{@{} r}{make} & a $\sim$ to
\\& $\sim$s
\end{tabular}
\item[-] control
\\have contrl / power over / of
\item[-] convenient
\\at sb\textquoteright s convenience
\item[-] conventional
\item[-] conversation \phantom{a} have a $\sim$ with
\item[-] convince
\\\begin{tabular}{@{} r | @{\hspace{0.1em}} l @{}}
\multicolumn{1}{@{} r}{sb be convinced} & that
\\& of sth
\end{tabular}
\\convincing
\item[-] cook \phantom{a} cooker 厨具
\item[-] cookie
\item[-] cool
\item[-] cooperate \phantom{a} $\sim$ with
\item[-] copy
\item[-] core
\\$\sim$ values 核心价值观
\item[-] corn
\item[-] corner
\\\begin{tabular}{@{} r | @{\hspace{0.1em}} l @{}}
be & drawing near
\\& around the corner
\\& on the way
\\& approaching
\end{tabular}
\item[-] corporate 公司的，法人的
\\corporation
\\$\underset{\text{\small 并入，融入}}{\text{incorporate}}$ A into B
\item[-] correct
\item[-] correspond
\\\textcircled{1} $\sim$ with sb 书信来往
\\\textcircled{2} $\sim$ with / to 相符合，一致
\\corresponding \emph{adj.} 相应的，相符合的
\\correspondent \emph{n.} 记者，通讯员
\\correspondence \emph{n.} 书信来往，通信
\item[-] cost \phantom{a} costly \emph{adj.} 昂贵的
\item[-] costume 戏服
\item[-] cottage 村舍
\item[-] cotton
\item[-] cough
\item[-] could
\item[-] council 委员会，地方议会
\item[-] count 
\\matter \emph{vi.} 重要，要紧，有重要关系
\item[-] country
\item[-] countryside
\item[-] county
\item[-] couple
\item[-] courage
\\courageous
\\encourage $\sim$ed $\sim$ing
\\discourage $\sim$ed $\sim$ing $\sim$ment
\item[-] course
\\\textcircled{1} 过程 in the course of
\\\textcircled{2} 航线，航道 \mbox{\small The ship was blown off the $\sim$.}
\\\textcircled{3} 一道菜 main course 主菜
\\\textcircled{4} 课程
\item[-] court 法庭；球场
\item[-] cousin
\item[-] cover
\\\emph{vt.} {\small\textcircled{1} 覆盖 be $\sim$ed with
\\\textcircled{2} 包含，包括，涵盖
\\\textcircled{3} 走完$\cdots$路程 I $\sim$ed 1km within 5min.
\\\textcircled{4} 新闻报道
\\\textcircled{5} 占地 $\sim$ an area of
\\\textcircled{6} 足以支付}
\item[-] coverage 新闻报道；覆盖范围
\item[-] cow
\item[-] crash
\item[-] crayon
\item[-] crazy
\item[-] cream
\item[-] create
\item[-] creative
\item[-] creature
\item[-] credit
\\\emph{n.} \textcircled{1}赊购\textcircled{2}贷款\textcircled{3}信用，信誉\\\textcircled{4}学分\textcircled{5}赞扬，称赞，认可
\\\emph{v.} \textcircled{1} be $\sim$ed as 被认为是\\\textcircled{2} be $\sim$ed to 归功于
\item[-] crew
\item[-] crime \emph{n.} \phantom{a} criminal \emph{n.} 罪犯
\\commit a $\sim$
\item[-] crisis \phantom{a} financial crisis
\item[-] criterion (\emph{pl.} criteria) \emph{n.} 标准
\item[-] critical \emph{adj.} 批判的；至关重要的
\item[-] criticise (criticize) \phantom{a} criticism
\item[-] crop
\item[-] cross
\\\emph{v.} \textcircled{1} 交叉
\\He stood there, with his arms $\sim$ed.
\\$\sim$ one\textquoteright s arms / legs
\\\textcircled{2}\begin{tabular}{@{ } l | @{\hspace{0.1em}} l @{}}
\multicolumn{1}{@{ } l}{sth} & cross \phantom{a} one\textquoteright s mind 突然想起
\\& come to / flash through
\end{tabular}
sth hit / occur to / strike sb
\item[-] crowd
\\crowded
\\crowd / flock / flood into 挤进，蜂拥而至
\item[-] crucial \phantom{a} vital critical
\item[-] cruel \phantom{a} cruelty \emph{n.}
\item[-] cry
\item[-] cuisine 烹饪，菜肴
\item[-] culture \phantom{a} cultural
\item[-] cup
\item[-] cupboard \phantom{a} cabinet
\item[-] cure
\\\emph{v.} cure sb of \phantom{a} treat sb for
\\\emph{n.} \begin{tabular}{@{} r @{ } c @{} @{ } l}
a & cure for & sth
\\& solution to
\end{tabular}
\item[-] curious{\small
\\curiosity
\\be curious about
\\arouse / stimulate one\textquoteright s curiosity about}
\item[-] current
\item[-] curtain
\\$\underset{\text{\small 拉开 \hspace{0.8em} 拉上}}{\text{part / draw}}$ the $\sim$
\item[-] custom \phantom{a} customs \emph{n.} 海关
\\\emph{n.} 风俗
\\\emph{adj.} 量身定制的
\\customize \emph{vt.} 给$\cdots$量身定制
\item[-] customer
\item[-] cut
\\\emph{v.} 切断；减少 cut the risk of
\\cut $\underset{\text{\small 砍倒 \hspace{0em} 切断 \hspace{0em} 切碎}}{\text{down / off / up}}$
\\cut the risk of
\\cut down on 减少
\\cut sth out from 从$\cdots$裁剪下来
\item[-] cute
\item[-] cycle
\item[-] caption
\item[-] carpenter
\item[-] carriage
\item[-] carrier
\item[-] cassette
\item[-] casual
\item[-] catastrophe \phantom{a} disaster
\item[-] cater
\\cater to one\textquoteright s needs/taste 迎合，满足：meet/satisfy
\item[-] caution
\\\emph{n.} 小心谨慎 \emph{v.} 告诫，提醒，警告
\\\emph{adj.} cautious
\item[-] ceremony
\item[-] chant
\item[-] chart
\item[-] choir
\item[-] circulate \emph{v.} 循环；（货币）流通
\\blood circulation
\item[-] claw
\item[-] clumsy
\item[-] coincidence 巧合
\\by $\sim$
\\what a $\sim$ that\ldots
\\coincide with 与$\cdots$一致；同时发生
\item[-] collision
\\A collide with B
\item[-] comb \emph{n.} 梳子 \emph{v.} 梳理
\item[-] command \emph{n.}命令，指挥，指示，控制
\\have a good $\sim$ / grasp of
\item[-] companion
\item[-] compromise
\\make a $\sim$
\item[-] compulsory 义务的，强制的
\item[-] condemn
\\\emph{v.} 谴责；判刑 sentence / $\sim$ sb to death
\item[-] confidential
\item[-] conscience
\item[-] consensus
\\reach a $\sim$
\item[-] conservative
\item[-] controversial
\item[-] convey
\item[-] corrupt \phantom{a} \emph{n.} corruption
\item[-] cosy (cozy)
\item[-] counter \emph{n.} 柜台；计算器
\item[-] curriculum (\emph{pl.} curricula)
\item[-] cushion
\item[-] cube
\item[-] cubic
\item[-] currency
\item[-] capture
\item[-] CE (Common Era)
\item[-] charm \phantom{a} charming
\item[-] childhood
\item[-] chip
\item[-] chore
\item[-] collaborate \phantom{a} collaboration
\item[-] compass
\item[-] (un)consious
\item[-] craft
\item[-] cucumber
\item[-] curve
\end{itemize}
\end{multicols}
\end{document}