% !TEX program = xelatex
\documentclass[../../book.tex]{subfiles}
\begin{document}
\section{D}
\raggedcolumns
\begin{multicols}{2}
\begin{itemize}
\item[-] daily
\\on a daily basis
\item[-] damage
\\do / cause damage to sb / sth
\item[-] damp
\item[-] dance
\\dance to music
\item[-] danger
\\in danger = at risk
\item[-] dangerous
\item[-] dare
\\daring \emph{adj.} 无畏的，敢于冒险的
\item[-] dark
\\dark / light blue
\item[-] data
\item[-] database
\item[-] date
\\\emph{n.}
\\\emph{v.} date with sb
\\make an appointment with
\item[-] daughter
\item[-] day
\item[-] dead \phantom{a} deadly \emph{adj.} 致命的
\\\emph{adj.} 死的 \emph{adv.} 完全，绝对
\item[-] deadline \phantom{a} meet the deadline 如期
\item[-] deaf
\\\begin{tabular}{@{} r | @{\hspace{0.1em}} l @{}}
\multicolumn{1}{@{} r}{turn a} & deaf ear to
\\& blind eye
\end{tabular}
\item[-] deal \phantom{a} \emph{n.} dealt
\\\emph{v.} deal with \textcircled{1} 解决，处理\\address/fix/attend to/approach
\\\textcircled{2} 与$\cdots$做生意\textcircled{3} 与$\cdots$打交道
\\\emph{n.} \textcircled{1} 大量 a great deal of [U]
\\\textcircled{2} 协议，交易 sign a deal with sb
\\\textcircled{3} It\textquoteright s not a big deal.
\\\textcircled{4} It\textquoteright s a deal. 就这么办吧
\item[-] dear
\item[-] death
\item[-] debate
\item[-] debt
\item[-] decade
\item[-] December
\item[-] decent 像样的，体面的，得体的
\item[-] decide \phantom{a} decide on sth
\item[-] decision
\item[-] declare
\\\textcircled{1} 宣布 \textcircled{2} 宣战 declare war on
\item[-] decline
\\\emph{v./n.} \textcircled{1} 减少，下降 on the $\sim$
\\\textcircled{2} 婉言谢绝 $\sim$ sth / to do
\item[-] decorate
\item[-] decrease \emph{v./n.} on the $\sim$
\item[-] deep \phantom{a} depth deepen
\item[-] deer [\emph{sing. / pl.}]
\item[-] defeat
\item[-] defence (defense) \phantom{a} defensive
\item[-] defend
\\$\sim$ against
\\$\sim$ sb from
\\$\sim$ sb 辩护
\item[-] definitely \phantom{a} definite
\item[-] definition \phantom{a} define \ldots{} as
\item[-] degree
\\\begin{tabular}{@{} r | @{\hspace{0.1em}} l @{}}
\multicolumn{1}{@{} r}{to} & some \phantom{a} degree
\\& a certain
\end{tabular}
\item[-] delay \emph{v./n.}
\\without delay
\\delay / postpone sth / doing
\item[-] delete
\item[-] delicate 脆弱的；易碎的；精致的；纤细的
\item[-] delicious
\item[-] deliver \phantom{a} \emph{n.} delivery
\\\textcircled{1} $\sim$ milk
\\\textcircled{2} $\sim$ a speech
\\\textcircled{3} $\sim$ a baby 接生
\item[-] demand
\\demand of sb to do sth
\\（表）in demand / need
\\demand for\ldots{} This area has a $\sim$ for water.
\item[-] demonstrate
\item[-] dentist
\item[-] deny
\\$\sim$ doing
\\It can\textquoteright t be denied that
\item[-] department
\item[-] departure \phantom{a} depart from
\item[-] depend
\\\begin{tabular}{@{} r | @{\hspace{0.1em}} l @{}}
\multicolumn{1}{@{} r}{be} & dependent on
\\& independent of
\end{tabular}
\item[-] depress \phantom{a} $\sim$ed $\sim$ing $\sim$ion
\item[-] depth
\item[-] describe
\item[-] description
\item[-] desert
\item[-] deserve
\item[-] design
\\by design = on purpose
\\\begin{tabular}{@{} r | @{\hspace{0.1em}} l @{}}
\multicolumn{1}{@{} r}{be designed} & to do 旨在
\\& for 针对
\end{tabular}
\item[-] desire
\\have a strong $\sim$ to do
\item[-] desk
\item[-] desperate \phantom{a} desperation \emph{n.}
\\渴望的；绝望的；拼命的；孤注一掷的
\item[-] despite
\\$\sim$ sth / doing
\\$\sim$ the fact that = although
\item[-] dessert
\item[-] destination
\item[-] destroy
\\destruction destructive
\item[-] detail \phantom{a} $\sim$ed \phantom{a} in detail
\item[-] detect
\item[-] detective 侦探
\item[-] determine
\\determination determined
\\$\sim$ / decide on
\item[-] develop
\\冲洗（胶卷）；感染，患；开发，研发；\\养成，习惯 $\sim$ a good habit of
\item[-] development
\item[-] device
\item[-] devote
\\be devoted to
\\devote oneself to doing
\item[-] diagram
\item[-] dialogue (dialog)
\item[-] diamond
\item[-] diary \phantom{a} keep a diary
\item[-] dictionary
\item[-] die
\item[-] diet \phantom{a} be on a diet
\item[-] differ
\item[-] difference
\item[-] different
\item[-] difficult
\item[-] difficulty
\item[-] dig (dug, dug) \phantom{a} dig into 深入
\item[-] digest \phantom{a} digestion
\item[-] digital \phantom{a} $\sim$ise
\item[-] dignity 尊严
\item[-] dimension 维度
\item[-] dining 进餐
\item[-] dinner 晚餐
\item[-] dinosaur
\item[-] direct
\\\emph{adj.} 直的 \emph{adv.} 径直
\\\mbox{directly \emph{adv.}直接 indirectly \emph{adv.}间接}
\\\emph{v.} \textcircled{1} 导演 director
\\\textcircled{2} 指引，指路，指导，管理，指示
\\be directed/targeted/aimed at 针对
\item[-] direction
\\in the direction of 朝
\\\begin{tabular}{@{} r | @{\hspace{0.1em}} l @{}}
\multicolumn{1}{@{} r}{under the} & direction of
\\& instruction / guidance
\end{tabular}
\item[-] director
\item[-] directory 电话号码簿，地址录
\item[-] dirty
\item[-] disability
\\enable \emph{vt.} \phantom{a} unable \emph{adj.} \phantom{a} disable \emph{vt.}
\item[-] disabled
\item[-] disappear
\\$\sim$ance
\\fade away
\item[-] disappointed
\\disapoint
\item[-] disaster \phantom{a} disastrous
\item[-] discipline \emph{n./v.} 处分，惩罚，纪律
\\self-discipline
\\disciplined \emph{adj.}
\item[-] discount
\\at a discount (of \ldots)
\item[-] discover
\item[-] discovery
\item[-] discrimination \phantom{a} racial $\sim$
\item[-] discuss
\item[-] discussion
\item[-] disease
\item[-] dish
\item[-] disk (disc)
\item[-] dismiss
\\解雇，裁员，开除 = lay off / fire
\item[-] display \phantom{a} on display
\item[-] distance \emph{n.} 距离 \emph{v.} 疏远
\\in the distance 在远处
\\at a distance 在不远处
\item[-] distant
\item[-] distinct \emph{adj.} 有区别的，不同的
\\distinction \emph{n.} 差别，区分，荣誉
\item[-] distinguish \emph{v.}区别，辨别 $\sim$ A from B
\\distinguishable \emph{adj.}能区别开的，能辨认出的
\\distinguished \emph{adj.}高贵的，尊贵的，杰出的
\\be $\sim$ed / celebrated for
\item[-] distribution \emph{n.} 分配
\\distribute \emph{v.}
\item[-] district 地区，行政区域
\item[-] disturb 打扰，妨碍，烦扰
\\$\sim$ed $\sim$ing $\sim$ance
\item[-] dive
\item[-] diverse
\\a diversity / variety of
\item[-] divide \phantom{a} divide into
\item[-] division \emph{n.} 分开；部门；部分；除法
\item[-] dizzy
\item[-] do
\item[-] docter
\item[-] document
\\\emph{v.} 记录 \phantom{a} documentary \emph{n.}
\\\emph{n.} 文档，文件 file
\item[-] dog
\item[-] dollar
\item[-] dolphin
\item[-] domain 领土，领域
\item[-] domestic 国内的，家用的，家庭的
\item[-] dominate \phantom{a} dominant \emph{adj.}
\item[-] donate \phantom{a} donation \emph{n.}
\item[-] door
\item[-] dormitory
\item[-] double
\\a double-edged sword
\item[-] doubt
\\\begin{tabular}{@{} r | @{\hspace{0.1em}} l @{}}
\multicolumn{1}{@{} r}{There is} & no doubt that \ldots
\\& some doubt whether \ldots
\end{tabular}
\item[-] down
\item[-] download \phantom{a} upload
\item[-] downstairs
\item[-] downtown
\item[-] dozen
\\dozens of \phantom{a} scores of
\item[-] draft = draw up 起草，拟定
\item[-] drag \phantom{a} drag sb away from
\item[-] dragon
\item[-] drama
\item[-] dramatic \mbox{\small 戏剧性的，急剧的，激动人心的}
\\dramatically \emph{adv.}
\item[-] draw (drew, drawn)
\\\textcircled{1} 画
\\\textcircled{2} 吸引 draw one\textquoteright s attention
\\\textcircled{3} 得出 draw a conclusion
\\\textcircled{4} 牵引 draw the curtains
\\\textcircled{5} 逼近 be drawing near
\\\textcircled{6} 取款 \textcircled{7} 平局
\item[-] drawer
\item[-] dream
\\$\sim$ of doing
\\$\sim$ away 虚度光阴
\\$\sim$ up 凭空想象，虚构 $\sim$ up a story
\item[-] dress
\\be / get dressed in
\\dress up (as \ldots)
\item[-] drill
\\\emph{vt.} \textcircled{1} 钻 $\sim$ a hole \emph{n.} 钻头
\\\textcircled{2} 培训，训练
\item[-] drink (drank, drunk)
\item[-] drive (drove, driven)
\\\textcircled{1} 驱使，驱动
\\\textcircled{2} 驱赶，赶走 $\sim$ sb away
\\\textcircled{3} drive sb mad
\item[-] driver
\item[-] drop
\\drop in $\left\{
\begin{array}{@{}l@{}}
\text{on sb} \\
\text{at sp}
\end{array}
\right.$
\\drop by \emph{vi.}
\\drop out of school
\\drop off \textcircled{1} 减少，下降
\\\textcircled{2} 小睡 take a nao
\\drop sb off at sp 让某人在某地下车
\item[-] drought \emph{n.} 干旱
\item[-] drug \phantom{a} abuse $\sim$
\item[-] dry \emph{adj./vt.} 干燥 $\sim$ clothes
\item[-] duck
\item[-] due to sth / doing
\\due \emph{adj.} \textcircled{1} due to 因为
\\\textcircled{2} 到期的
\\\textcircled{3} 预计的，预期的 \\\phantom{aaa}be $\sim$ / scheduled to do
\\\textcircled{4} 恰当的，合适的 \\\phantom{aaa}proper appropriate
\\\emph{adv.} duly \phantom{a} {\color{violet}truly}
\item[-] dumpling
\item[-] duration 持续 \phantom{a} during \emph{prep.}
\item[-] during
\item[-] dust \phantom{a} dusty
\item[-] duty
\item[-] dynamic
\item[-] dynasty
\item[-] dash
\\\textcircled{1} rush / charge 疾奔，猛冲
\\\textcircled{2} 猛撞，猛击 $\sim$ against
\item[-] dawn \emph{n.} 黎明，拂晓
\\dusk \emph{n.} 黄昏，傍晚 at dawn / dusk
\item[-] delight \emph{vt./n.} 开心 $\sim$ed $\sim$ful
\\take $\sim$ in
\item[-] deliberately
\\= on purpose = by design \\= intentionally
\item[-] deposit 
\\\emph{n.} \textcircled{1} 沉淀 \textcircled{2} 存款
\\\emph{vt.} \textcircled{1} 使沉淀 \textcircled{2} 存钱 withdraw from
\\\textcircled{3} 寄存，存放 \textcircled{4} 放置 = lay 
\item[-] dial \emph{vt.} 拨号
\item[-] dilemma \emph{n.} 困境，窘境
\item[-] dioxide
\item[-] dip 蘸
\item[-] diploma 文凭，学位证书
\item[-] discourage \emph{vt.}
\item[-] disgust \emph{vt.} 使恶心 $\sim$ed $\sim$ing
\item[-] divorce \phantom{a} $\sim$ed
\item[-] doll
\item[-] dot \emph{n./v.} be dotted with
\item[-] drawback = downside 缺点
\\shortcoming weakness
\item[-] drum
\item[-] drunk \emph{adj.}
\item[-] dull \emph{adj}
\item[-] dustbin \emph{n.} 垃圾箱
\item[-] dam
\item[-] dedicate
\item[-] drone
\item[-] drown
\end{itemize}
\end{multicols}
\end{document}