% !TEX program = xelatex
\documentclass[../../book.tex]{subfiles}
\begin{document}
\section{E}
\raggedcolumns
\begin{multicols}{2}
\begin{itemize}
\item[-] each
\item[-] eager \phantom{a} $\sim$ness
\\\begin{tabular}{@{} r | @{\hspace{0.1em}} l | @{\hspace{0.1em}} l @{}}
\multicolumn{1}{@{} r}{be} & \multicolumn{1}{@{\hspace{0.1em}} l}{$\sim$} & to do
\\& anxious & for
\\& \multicolumn{1}{@{\hspace{0.1em}} l}{desperate}
\end{tabular}
\item[-] eagle 鹰
\item[-] ear \phantom{a} turn a deaf ear to
\item[-] early
\\at an early age 在小时候
\item[-] earn 挣钱，赢得
\\earn one\textquoteright s living 谋生
\item[-] earth
\\on earth 究竟，到底
\item[-] earthquake
\\an $\sim$ break out
\item[-] ease
\\\emph{vt.} 缓解，减轻
\\relieve / ease one\textquoteright s pain / stress
\\\emph{n.} feel at ease 轻松，惬意
\\with ease 简单地，不费力地
\item[-] east
\item[-] eastern
\item[-] easy \emph{opp.} uneasy
\\简单的；惬意的
\item[-] eat (ate, eaten)
\item[-] ecology \phantom{a} ecologist ecological
\item[-] economic
\\{\small economy economics economist ecnomical}
\item[-] edge
\\on the edge of
\\a double-edged sword
\\edge up to sp = inch to/towards sp
\item[-] edition 版本
\item[-] editor
\item[-] education
\\educate educated educational
\item[-] educator \phantom{a} educationalist
\item[-] effect
\\have an effect on
\\effective
\\side effect
\\in effect 生效的
\item[-] efficient \phantom{a} efficiency
\item[-] effort
\\make an effort to do
\item[-] egg \phantom{a} lay eggs
\item[-] eight
\item[-] eighteen
\item[-] eighth
\item[-] eighty
\item[-] either
\item[-] elder \emph{adj.}
\item[-] elderly \emph{adj.} \phantom{a} the elderly
\item[-] election \phantom{a} elect \phantom{a} {\color{violet}select}
\item[-] electricity \phantom{a} electric electrical
\item[-] electronic
\item[-] elegant \phantom{a} elegance
\item[-] element
\item[-] elephant
\item[-] eleven
\item[-] else
\item[-] elsewhere
\item[-] email
\item[-] embarrassed
\\embarrass embarrassment
\item[-] emerge
\\emergence \phantom{a} {\color{violet}occurence}
\item[-] emergency
\item[-] emotion
\item[-] emperor
\item[-] emphasis
\\emphasize sth / doing
\\lay emphasis on
\\attach significance to
\item[-] employ
\\\textcircled{1} {\small (un)employment employer employee}
\\\textcircled{2} 使用，应用，雇用 apply
\item[-] empty \phantom{a} $\sim$ the dustbin
\item[-] enable
\item[-] encounter
\\run / come across
\item[-] encourage
\item[-] end
\\endless
\\end in failure / divorce
\\end up doing
\\end with 用$\cdots$结束（poetry/song/\ldots）
\item[-] enemy
\item[-] energetic
\item[-] energy
\item[-] engage
\item[-] engine
\item[-] engineer
\item[-] England
\item[-] English
\item[-] enhance
\\enhance our cultural confidence
\item[-] enjoy
\\-able -ment
\\$\sim$ yourself
\item[-] enormous \phantom{a} an $\sim$ wave
\item[-] enough
\\ample adequate sufficient
\item[-] ensure \phantom{a} guarantee
\item[-] enter \phantom{a} entrance \emph{n.} 通道，入口
\item[-] enterprise
\item[-] entertainment \phantom{a} entertain -ed -ing
\item[-] enthusiastic
\\be $\sim$ about
\\enthusiastically
\\enthusiasm
\\enthusiast 热情的人
\item[-] entirely
\item[-] entitle
\\\textcircled{1} {\small 给$\cdots$(物)命名 name A(人) after B}
\\\textcircled{2} 给$\cdots$资格
\item[-] entry \emph{n.} 进入；参赛作品
\item[-] envelope \phantom{a} envelop
\item[-] environment
\\environmental environmentalist
\\environmentally friendly
\item[-] envy \phantom{a} envious jealous
\item[-] episode
\item[-] equal \phantom{a} (in)equality
\item[-] equator
\item[-] equipment
\\equip / arm sb with
\\sb be equipped with
\item[-] era
\item[-] eraser \emph{n.} 橡皮擦，黑板擦
\\erase \emph{v.} 擦除
\item[-] error
\item[-] erupt \phantom{a} eruption
\item[-] escape
\\\textcircled{1} $\sim$ from 逃跑
\\\textcircled{2} \emph{vi.} 泄露
\\\textcircled{3} sth $\sim$ sb 被忘记
\\\textcircled{4} $\sim$ sth / doing 逃避
\item[-] especially = particularly
\item[-] essay 短文，散文，随笔
\item[-] essential
\\\emph{adj.} be $\sim$ to
\\\emph{n.} 必需品 necessity
\item[-] establish \phantom{a} $\sim$ment
\item[-] estate
\\property \emph{n.} 财产；房地产
\item[-] estimate
\\overestimate underestimate
\\estimation
\item[-] Europe
\item[-] European
\item[-] evaluate
\item[-] eve
\\on Christmas Eve
\item[-] even
\\\emph{adv.}\textcircled{1}甚至\textcircled{2}+\emph{adj.}-er $\sim$/still/far/\ldots
\\\emph{adj.} 平坦的，平静的，水平的
\\\phantom{adj.} uneven = rough
\item[-] evening
\item[-] event 比赛项目；大事件；有意义的事情
\item[-] eventually
\item[-] ever
\item[-] every
\item[-] everybody
\item[-] everyday
\item[-] everyone
\item[-] everything
\item[-] everywhere
\item[-] evidence \phantom{a} proof evident
\item[-] exactly
\item[-] exam (examination)
\item[-] examine
\item[-] example
\\for example
\\\begin{tabular}{@{} r | @{\hspace{0.1em}} l @{}}
\multicolumn{1}{@{} r}{take \ldots} & for $\sim$
\\& as an $\sim$
\end{tabular}
\item[-] excellent \phantom{a} excellence
\item[-] except
\item[-] exceptional \phantom{a} -ly
\item[-] exchange
\\$\sim$ sth with sb
\\$\sim$ A for B 用 A 交换 B
\\in exchange for
\\an exchange student
\item[-] excited
\item[-] exciting
\item[-] excuse
\item[-] exercise
\item[-] exhibition
\\on $\sim$
\\exhibit
\item[-] exist
\\come into being / existence
\item[-] exit \emph{n.} 出口 \emph{v.} 退出；离去
\item[-] expand \phantom{a} $\sim$ our vocabulary
\item[-] expansion
\item[-] expect
\item[-] expectation
\item[-] expense
\\\begin{tabular}{@{} r | @{\hspace{0.1em}} l @{}}
\multicolumn{1}{@{} r}{at the} & $\sim$ of
\\& price
\\& cost
\\& sacrifice
\end{tabular}
\item[-] (in)expensive
\item[-] experience \phantom{a} (in)experienced
\item[-] experiment
\\\emph{v.} $\sim \underset{\text{\small 尝试 \hspace{0.1em} 试验}}{\text{with / on}}$
\\\emph{n.}
\item[-] expert
\item[-] explain \phantom{a} explanation
\\account for
\item[-] explode
\\$\sim$ with anger
\\explosion explosive
\item[-] explore
\\exploration {\color{violet}adoration storage}
\item[-] export \phantom{a} import
\item[-] expose
\\$\sim$ oneself to
\\be $\sim$ed to
\item[-] exposure
\item[-] express \emph{v.} \phantom{a} \emph{adj.} 快速的
\\expression 表情；表达
\\expressive \emph{adj.}{\small 有表现力的；表达$\cdots$的}
\item[-] extend
\item[-] extension \phantom{a} extensive
\item[-] extent
\\\begin{tabular}{@{} r | @{\hspace{0.1em}} l @{}}
\multicolumn{1}{@{} r}{to} & a certain extent / degree
\\& some
\end{tabular}
\item[-] external
\item[-] extinction \phantom{a} extinct \emph{adj.}
\\die out 灭绝
\item[-] extra
\item[-] extraordinary
\item[-] extremely
\\go to extremes
\item[-] eye
\\catch one\textquoteright s eye
\\fix one\textquoteright s eyes on
\\turn a blind eye to
\\keep an eye on
\\make eye contact with sb
\item[-] embassador
\item[-] embassy
\item[-] enlarge \phantom{a} {\color{violet}enrich}
\item[-] enquire
\\enquire $\left\{
\begin{array}{@{}l@{}}
\text{about sth / sb} \\
\text{into sth = investigate}
\end{array}
\right.$
\item[-] enquiry
\item[-] evolve \phantom{a} evolution
\item[-] electric
\item[-] elevator
\item[-] eliminate
\item[-] empathy
\item[-] empress
\item[-] endangered
\item[-] ethical
\item[-] ethnic
\item[-] exceed
\item[-] exhaust
\end{itemize}
\end{multicols}
\end{document}