% !TEX program = xelatex
\documentclass[../../book.tex]{subfiles}
\begin{document}
\section{F}
\raggedcolumns
\begin{multicols}{2}
\begin{itemize}
\item[-] fabric
\\\textcircled{1} 布料，织物
\\\textcircled{2} （建筑物）结构
\item[-] face
\\be faced / confronted with
\\encounter
\item[-] facilitate
\\\textcircled{1} 促进，推动 
\\$\sim$ our well-rounded development
\\\textcircled{2} 使便利
\item[-] facility
\item[-] fact
\\in fact = as a matter of fact
\item[-] factor
\item[-] factory
\item[-] fail \phantom{a} fail to do
\\（势力）减退，（电力）故障
\item[-] failure
\item[-] fair
\\\emph{adj.} 公平的 \emph{n.} 集市，交易会
\item[-] faith
\\\begin{tabular}{@{} r | @{\hspace{0.1em}} l @{}}
\multicolumn{1}{@{} r}{I have faith} & that \ldots
\\& in sb
\end{tabular}
\\be faithful to sb {\small 对$\cdots$忠贞不渝/诚实}
\item[-] fall (fell, fallen)
\item[-] false
\item[-] familiar \phantom{a} -ise
\\A be familiar with B A 熟悉 B
\\B be familiar to A
\item[-] family
\item[-] famous
\\rise to fame
\\\begin{tabular}{@{} r | @{\hspace{0.1em}} l @{}}
\multicolumn{1}{@{} r}{be} & famous as/for
\\& noted/celebrated/well-known
\end{tabular}
\item[-] fan
\item[-] fancy
\item[-] fantastic \emph{adj.}
\item[-] fantasy \emph{n.} 幻想，想象
\item[-] far (farther/further, farthest/furthest)
\\have a far-reaching effect on
\\far too + \emph{adj./adv.} 极其，非常
\\far from 远非，远离
\item[-] farm
\item[-] farmer
\item[-] fashion
\\in / out of fashion
\\fashionable trendy stylish
\\sth catch on 变得流行
\item[-] fast
\item[-] fat
\item[-] father (dad)
\item[-] fault \phantom{a} \emph{adj.} faulty
\\find fault with sb 挑剔，找茬
\\be particular about
\item[-] favour (favor)
\\do sb a favor
\\ask a favor of sb
\\in favor of
\item[-] favourite (favorite)
\item[-] fear
\\\emph{adj.} fearless = daring \phantom{a} fearful
\\in fear of sth / doing
\\for fear that
\item[-] feature
\item[-] February
\item[-] fee \phantom{a} tuition fee 学费
\item[-] feed (fed, fed)
\\feed on
\\be fed up with
\item[-] feel
\item[-] feeling
\item[-] fellow
\item[-] female \phantom{a} male
\item[-] fence \emph{vi.} 击剑 \emph{n.} 栅栏
\item[-] festival
\item[-] fetch
\item[-] fever
\item[-] few
\item[-] fibre (fiber)
\item[-] fiction
\item[-] field
\\track and field
\\in the field of
\item[-] fifteen
\item[-] fifth
\item[-] fifty
\item[-] fight (fought, fought)
\\fight back 抑制，阻碍
\item[-] figure
\\\emph{v.}\textcircled{1}{\small 认为 I figure/assume/suppose that}
\\\textcircled{2} 理解，弄明白，算出，得出，想出
\\\phantom{aa} figure out \phantom{a} make sense of
\\\emph{n.} 人物，身份，体型，轮廓，数字
\item[-] file \phantom{a} document
\item[-] fill
\item[-] film
\\\emph{v.} 拍摄 shoot (shot, shot)
\\\emph{n.} 电影；胶卷 develop a roll of film
\item[-] finally
\\final
\item[-] finance \emph{n.} 资金，金融 \emph{v.} 资助
\item[-] financial
\item[-] find
\item[-] finding
\item[-] fine \phantom{a} fine sb -money
\item[-] finger
\item[-] finish
\item[-] fire
\\\textcircled{1} 解雇，裁员 \begin{tabular}{@{} r @{} | @{\hspace{0.1em}} l @{}}
\multicolumn{1}{@{} r @{}}{} & fire sb
\\& dismiss / lay off
\end{tabular}
\\\textcircled{2} 开火
\item[-] firm
\\I hold a firm belief that
\item[-] first
\item[-] fish
\item[-] fisherman
\item[-] fist
\\curl into a fist
\item[-] fit
\\fitness 健康
\\be fitted with 被$\cdots$安装 \\\phantom{aa} The tail was $\sim$ed with a cinema.
\\be fit / suitable for / to do 适合
\item[-] five
\item[-] fix 固定，修理，解决
\\fix a problem
\\fix one\textquoteright s mind
\item[-] flag
\\a flag-raising ceremony
\item[-] flash
\\sth flash through one\textquoteright s mind
\\in a flash
\item[-] flat
\\a flat tyre \phantom{a} uneven = rough
\item[-] flavour (flavor)
\item[-] flexible \phantom{a} -bility
\item[-] flight
\item[-] flood
\item[-] floor
\item[-] flour 面粉
\item[-] flow \phantom{a} flew
\item[-] flower \emph{v.} blossom
\item[-] flu
\item[-] fluent \phantom{a} fluency
\item[-] fly (flew, flown)
\item[-] focus
\\focus / concentrate on
\\focused / concentrated
\item[-] foggy \phantom{a} fog
\item[-] fold \phantom{a} unfold
\item[-] folk \phantom{a} $\sim$ music
\item[-] follow
\\as follows
\\follower
\\follow suit
\\follow one\textquoteright s footsteps
\item[-] fond
\\be fond of
\item[-] food
\item[-] foot (\emph{pl.} feet)
\item[-] football
\item[-] for
\item[-] force
\\force / press sb to do sth
\\by force
\item[-] forecast \phantom{a} weather forecast
\item[-] forehead 前额
\item[-] foreign \phantom{a} foreigner
\item[-] forest
\item[-] forever
\item[-] forget
\\forgetful 健忘的
\\unforgettable
\item[-] forgive (forgave, forgiven) forgiveness
\item[-] fork
\item[-] form
\\\emph{v.} \phantom{a} formation
\\\emph{n.}\textcircled{1}application form\\\phantom{\emph{n.}}\textcircled{2}in/take the form of
\item[-] (in)formal
\item[-] format
\item[-] former \phantom{a} the former / latter
\item[-] fortunately \phantom{a} fortune
\item[-] forty \phantom{a} in one\textquoteright s forties
\item[-] forward
\\look forward to doing
\\step forward/backward/eastward/into/\ldots
\item[-] found
\item[-] foundation
\item[-] fountain 泉水
\\spring (sprang, sprung) spring to one\textquoteright s feet
\item[-] four
\item[-] fourteen
\item[-] fourth
\item[-] fox
\item[-] France
\item[-] frank = honest
\\To be frank, / Frankly speaking,
\item[-] free
\\\textcircled{1}
\\\textcircled{2}be free of charge
\\\textcircled{3}be free of/from 免于$\cdots$侵害/影响
\\\textcircled{4} tax-free
\item[-] freedom
\item[-] freeze (froze, frozen)
\\$\sim$ in astonishment
\item[-] French
\item[-] frequency
\item[-] frequently
\item[-] fresh \phantom{a} refresh one\textquoteright s mind
\item[-] friction 摩擦力
\item[-] Friday
\item[-] fridge (refrigerator)
\item[-] friend
\item[-] friendly \phantom{a} friendliness
\item[-] friendship
\item[-] frightened
\item[-] frog
\item[-] from
\item[-] front
\\in front of
\\in the front of
\item[-] frontier
\\\textcircled{1}尖端学科，新领域
\\\textcircled{2}国界，边境 border / boundary
\item[-] frost \phantom{a} frosty
\item[-] fruit \phantom{a} fruitful / -less
\item[-] fry
\item[-] fuel \phantom{a} fuel my appetite
\item[-] full \phantom{a} be $\sim$ of
\item[-] fun
\item[-] function \emph{v./n.}
\\functional \emph{adj.}
\item[-] fund \emph{v.} 资助 \emph{n.} 资金
\item[-] fundamental \emph{adj.} 根本的，基本的
\item[-] funny
\item[-] furniture
\\a set / piece of $\sim$
\item[-] further
\item[-] future
\item[-] facial
\item[-] fade \emph{v.} fade away
\item[-] fare 交通费用，车费，票价
\item[-] fasten
\\fasten / tie A to B
\item[-] fax 传真
\item[-] feather 羽毛
\item[-] feast
\\be a visual $\sim$ for your eyes
\item[-] federal \phantom{a} $\sim$ government
\item[-] ferry \emph{v./n.} 摆渡，渡船
\item[-] fierce
\item[-] firework
\item[-] flame
\\\emph{vi.}\textcircled{1}燃烧\\\phantom{\emph{vi.}}\textcircled{2}通红{\small Her cheeks flamed with rage.}
\\\emph{n.} add fuel to the flames (of \ldots)
\\\phantom{\emph{n.}} be in flames = be on fire
\\\phantom{\emph{n.}} burst into flames
\item[-] flee (fled, fled)
\item[-] flesh \phantom{a} in the flesh
\item[-] foolish
\item[-] forbid (forbade, forbidden)
\\forbid sb to do / from doing
\item[-] foresee (foresaw, foreseen)
\item[-] fortnight 两周（十四天）
\item[-] foster 培养，养育，抚育
\\foster our interests
\item[-] fox
\item[-] fragile
\\\textcircled{1} weak（人）
\\\textcircled{2} 易碎的，易损的
\item[-] fragrant 芬芳的 \phantom{a} -ce
\item[-] framework
\item[-] freeway \emph{n.}
\item[-] frighten
\item[-] fright
\item[-] funeral
\item[-] fur
\item[-] furnished
\item[-] fable
\item[-] faint
\item[-] fascinating
\item[-] fertile
\item[-] fireman (\emph{pl.} firemen)
\item[-] float
\item[-] fog
\item[-] fool
\item[-] fortune
\item[-] frame
\item[-] fulfil(l)
\item[-] furthermore
\end{itemize}
\end{multicols}
\end{document}