% !TEX program = xelatex
\documentclass[../../book.tex]{subfiles}
\begin{document}
\section{G}
\raggedcolumns
\begin{multicols}{2}
\begin{itemize}
\item[-] gain \phantom{a} No pains, no gains.
\item[-] gallery 画廊，艺术长廊
\item[-] game
\item[-] gap
\\generation gap
\\bridge the gap between A and B
\item[-] garbage \phantom{a} garbage bin/can
\item[-] garden
\item[-] garlic 蒜 \phantom{a} union 洋葱
\item[-] gas
\item[-] gate
\item[-] gather
\\gather speed \phantom{a} accelerate
\\$\sim$ one\textquoteright s courage to do
\\$\sim$ around
\\family gathering
\item[-] gender
\item[-] general
\\\emph{n.} \textcircled{1} 将军
\\\textcircled{2} in general \phantom{a} generally speaking
\item[-] generate
\\\begin{tabular}{@{} r | @{\hspace{0.1em}} l @{}}
\multicolumn{1}{@{} r}{generate} & new ideas
\\& electricity
\end{tabular}
\item[-] generation
\item[-] generous \phantom{a} generosity
\item[-] genius
\item[-] gentle \phantom{a} gently
\item[-] gentleman
\item[-] genuine \emph{adj.} 非伪造的，真正的
\item[-] geography
\item[-] geometry 几何
\item[-] German
\item[-] Germany
\item[-] get
\item[-] gift \phantom{a} have a gift/talent for
\item[-] gifted \phantom{a} be gifted in
\item[-] giraffe
\item[-] girl
\item[-] give (gave, given)
\item[-] glad
\item[-] glass
\item[-] global
\\globalise globalised globalisation
\item[-] globe
\item[-] glove
\item[-] glue
\\\begin{tabular}{@{} r @{} l  @{\hspace{0.4em}} l @{}}
& glue one\textquoteright s eyes & to
\\& fix & on
\end{tabular}
\item[-] go
\item[-] goal
\item[-] goat
\item[-] gold
\\\emph{n.} 金 \emph{adj.} 金的 \phantom{a} golden \emph{adj.} 金色的
\item[-] golf
\item[-] good
\item[-] goodbye (bye) \phantom{a} say $\sim$ to
\item[-] goods [\emph{pl.}] 商品
\\{\color{violet}manners surroundings belongings\\possessions instructions}
\item[-] government
\\govern \emph{v.} 控制，统治
\\\phantom{aaaaaa} monitor dominate rule
\item[-] grab
\item[-] grade \emph{n./vt.}
\item[-] gradually
\item[-] graduate
\item[-] grain
\item[-] grammar
\item[-] gramme (gram)
\item[-] grand 宏伟的，豪华的 \phantom{a} -ness
\item[-] granddaughter
\item[-] grandfather (grandpa)
\item[-] grandmother (grandma)
\item[-] grandparent
\item[-] grandson
\item[-] grape
\item[-] grasp 紧紧抓住；掌握；理解，领会
\\have a good grasp of
\item[-] grass
\item[-] grateful = thankful
\\be $\sim$ to sb for sth
\\\emph{n.} gratefulness / gratitude
\item[-] gravity
\item[-] great
\item[-] greedy \phantom{a} greed
\item[-] green \phantom{a} a green hand 新手
\item[-] greenhouse
\item[-] greet \phantom{a} \emph{n.} greeting
\\be greeted by/with
\item[-] grey
\item[-] grocery 食品杂货店
\\groceries 食品杂货
\item[-] ground \phantom{a} be rooted to the $\sim$/spot
\item[-] group
\\\emph{vt.} 分组
\\\emph{n.} in groups
\item[-] grow(grew, grown) \phantom{a} growth
\\\emph{vt.} \textcircled{1} 增加 \textcircled{2} \emph{linking v.} 变得
\item[-] guarantee \emph{v./n.}
\\be under guarantee 在保修期内
\item[-] guard
\\a guard dog
\\on guard 在放哨，在值班
\item[-] guess \phantom{a} \emph{n.} guessing
\item[-] guest \phantom{a} host
\item[-] guidance
\\under the guidance of
\item[-] guide
\\\emph{vt.}
\\\emph{n.} \textcircled{1} 导游 \textcircled{2} 指南 a guide to sp
\item[-] guideline 指导方针，准则
\item[-] guilty \emph{adj.} 内疚的，有负罪感的
\\{}[\emph{opp}] innocent
\item[-] guitar
\\guitarist pianist musician
\item[-] gun \phantom{a} aim the gun at
\item[-] guy
\item[-] gym
\item[-] gymnastics \phantom{a} gymnast 体操运动员
\item[-] garage \emph{n.} 车库；修理厂
\item[-] garment \emph{n.} 衣服
\item[-] gesture
\item[-] glance \phantom{a} glance at
\item[-] glare \phantom{a} glare at
\item[-] glory \phantom{a} glorious
\item[-] gradual
\item[-] graph \phantom{a} chart diagram
\item[-] gene
\item[-] giant
\item[-] god
\item[-] graceful
\item[-] gratitude
\end{itemize}
\end{multicols}
\end{document}