% !TEX program = xelatex
\documentclass[../../book.tex]{subfiles}
\begin{document}
\section{H}
\raggedcolumns
\begin{multicols}{2}
\begin{itemize}
\item[-] habit
\\\begin{tabular}{@{} r  @{ } l  @{ } l @{}}
get rid of / remove & the & bad habit of
\\develop / form & & good
\end{tabular}
\item[-] habitat
\item[-] hair \phantom{a} hairless
\item[-] half (\emph{pl.} halves)
\\{\color{violet}proofs roofs beliefs safes}
\item[-] hall
\item[-] ham
\item[-] hamburger
\item[-] hand
\\hands-on \emph{adj.} 动手的，实际操作的 \\\phantom{aaaaaaaaaaa..} $\sim$ ability
\\by hand \phantom{a} with a/my hand/-s
\item[-] handbag
\item[-] handkerchief
\item[-] handle
\\\emph{v.} 解决，处理，对付；触，拿
\\\emph{n.} 把手
\item[-] handsome
\item[-] handwriting
\item[-] hang
\\\emph{v.}\textcircled{1}(hanged, hanged) 绞死，吊死
\\\phantom{\emph{v.}}\textcircled{2}(hung, hung)
\\\phantom{\emph{v.}\textcircled{2}}1. hang out 闲逛
\\\phantom{\emph{v.}\textcircled{2}}2. 悬挂
\\\phantom{\emph{v.}\textcircled{2}}\mbox{3. hang/hold on (to) 坚持，别挂断}
\item[-] happen \phantom{a} \emph{n.} happening
\\happen to do
\\It happens that
\\sth happen to sb
\item[-] happy
\item[-] hard \emph{adj./adv.} 坚硬的，勤奋的
\\harden \emph{vt.}
\item[-] hardly \phantom{a} Hardly \ldots{} when \ldots
\item[-] harm
\\do good / harm to
\\be harmful to
\\be good / bad for
\item[-] harmful
\item[-] harmonious
\item[-] harmony \phantom{a} in harmony
\\get on in harmony with 和谐相处；吻合
\item[-] harvest \emph{v./n.}
\item[-] hat
\item[-] hatch
\item[-] hate
\item[-] have (has)
\item[-] he
\item[-] head
\\head for / to / towards / into / \ldots
\\{\color{violet}edge up to \phantom{a} inch towards}
\item[-] headache
\item[-] health
\item[-] healthy
\item[-] hear (heard, heard)
\item[-] heart
\\lose heart
\\form the bottom of one\textquoteright s heart
\\heartful \emph{adj.} 由衷的
\\stone-hearted warm-hearted
\item[-] heat \emph{v./n.}
\item[-] heavy \phantom{a} heavily
\item[-] height \phantom{a} heighten
\\{\color{violet}lengthen strengthen weight}
\item[-] hello
\item[-] help
\\with the help of
\\with one\textquoteright s help
\item[-] helpful
\item[-] hen 母鸡 \phantom{a} cock \emph{n.} 公鸡
\item[-] hence
\item[-] her
\item[-] herb
\item[-] here
\item[-] hero
\item[-] hers
\item[-] herself
\item[-] hesitate
\\don\textquoteright t hesitate to do
\\without hesitation
\\be hesitant over / about
\item[-] hi
\item[-] hide (hid, hidden) \phantom{a} hide A from B
\item[-] high
\item[-] highlight
\\\emph{n.}
\\\emph{vt.} underline the fact that
\item[-] hike
\item[-] hill
\item[-] him
\item[-] himself
\item[-] hire
\item[-] his
\item[-] historic \emph{adj.} 具有历史意义的
\\historical \emph{adj.} 有关历史的
\item[-] history \phantom{a} historian
\item[-] hit
\\an Internet hit
\\make a hit
\\It hit sb that
\item[-] hobby
\item[-] hold (held, held)
\item[-] hole
\\$\underset{\text{\small (dug, dug)}}{\text{dig}}$ a hole
\item[-] holiday \phantom{a} on holiday / vacation
\item[-] home
\\be home to
\\hit home to sb 使某人感受到重要性
\item[-] hometown
\item[-] homework
\item[-] honest \phantom{a} (dis)honesty
\item[-] honey
\item[-] honour (honor) \emph{v.} 纪念，尊重
\\in honor / memory of
\\It is my great honor to do
\\I\textquoteright m honored to do
\item[-] hope \phantom{a} -ful -less
\\hope for sth
\\hope to do
\\with sb sth / to do
\item[-] horrible \phantom{a} horror
\item[-] horse
\item[-] hospital \phantom{a} in (the) hospital
\\{\color{violet}hospitable 热情的，好客的\\hospitality \emph{n.} 热情好客}
\item[-] host / hostess
\item[-] hot
\item[-] hotel
\item[-] hour
\item[-] house \phantom{a} accommadate
\item[-] household \emph{n./adj.}
\item[-] housework
\item[-] housing \emph{n.} 住宅；住房建设
\item[-] how
\item[-] however
\item[-] hug
\item[-] huge
\item[-] human
\item[-] humble \phantom{a} humbly \phantom{a} modest
\item[-] humorous \phantom{a} humor
\item[-] hundred
\item[-] hungry
\\be hungry for
\\hunger \emph{v./n.} hunger for
\item[-] hunt \begin{tabular}{@{} r | @{\hspace{0.1em}} l @{}}
\multicolumn{1}{@{} r}{} & hunt \phantom{a} for
\\& seek (sought, sought)
\end{tabular}
\item[-] hurricane
\item[-] hurry \phantom{a} in a hurry / rush
\item[-] hurt
\item[-] husband
\item[-] hydrogen
\item[-] hammer \phantom{a} $\sim$ a nail
\item[-] handful \phantom{a} a $\sim$ of
\item[-] handy \emph{adj.} 轻便的，便携的
\item[-] harbor
\\\emph{n.} 港口；避风港
\\\emph{v.} shelter 庇护，为$\cdots$提供住所
\item[-] hardship
\item[-] headline
\\make the headline 成为头条
\item[-] heel \emph{n.} 鞋跟；脚后跟
\\high-heeled shoes
\item[-] helicopter
\item[-] helmet
\item[-] hook \emph{v./n.}
\\be hooked on 被$\cdots$迷住，迷上
\item[-] howl
\item[-] heritage
\item[-] highway
\item[-] horror
\item[-] hostess
\item[-] humanity
\item[-] humour (humor)
\item[-] hybrid
\end{itemize}
\end{multicols}
\end{document}