% !TEX program = xelatex
\documentclass[../../book.tex]{subfiles}
\begin{document}
\section{I}
\raggedcolumns
\begin{multicols}{2}
\begin{itemize}
\item[-] I
\item[-] ice \phantom{a} icy
\item[-] ice-cream
\item[-] idea
\item[-] ideal \phantom{a} $\sim$ university
\item[-] identical \emph{adj.} 完全相同的；同卵的
\item[-] identify \emph{v.} $\sim$ \ldots{} as
\item[-] identity \emph{n.} 身份；特征
\\identity card 身份证
\\identification 身份证明
\item[-] idiom
\\As the saying / idiom goes, \ldots
\item[-] if
\item[-] ignore
\\ignorance \emph{n.} 忽视；无知
\\ignorant \emph{adj.} 无知的
\item[-] ill \phantom{a} illness
\item[-] illegal \phantom{a} legal
\item[-] illness
\item[-] illustrate 说明，证明；插图
\\illustration
\item[-] image
\item[-] imagine
\\imagine doing sth
\\imaginative 想象力丰富的
\\imaginable 可想象的
\\imaginary 虚构的
\\imagination \emph{n.}
\\beyond / out of imagin
\item[-] immediately
\\$\sim$ / instantly / directly 一$\cdots$就$\cdots$
\item[-] impact
\\have an $\sim$ / influence / effect on
\item[-] imply 暗示 \phantom{a} implication \emph{n.}
\item[-] import \phantom{a} export
\item[-] important
\\attach importance / significance to
\\lay emphasis on
\item[-] impossible
\item[-] impress \phantom{a} impressive
\\sb be impressed by/with sth
\item[-] impression
\\sth leave a \ldots impression on sb
\item[-] improve \phantom{a} improvement
\item[-] in
\item[-] inch \emph{v.}
\\I can\textquoteright t move a inch. 
\\inch towards sp
\item[-] incident
\item[-] include
\\including \emph{prep.}
\\included \emph{adj.}
\\inclusive \emph{adj.} 包容的
\item[-] income
\item[-] increase
\\on the increase / decrease / \ldots
\item[-] incredible
\item[-] indeed
\\A friend in need is a friend indeed.
\item[-] independent
\\be independent of
\\be dependent on
\item[-] India
\item[-] Indian
\item[-] indicate \emph{v.} 表明，象征
\item[-] individual \phantom{a} group
\item[-] industry \phantom{a} industrial 工业的
\\{\color{violet}industrious = diligent}
\item[-] infection
\\be infected / affected with
\\infectious
\item[-] infer 推断
\\make an inference
\item[-] influence
\item[-] influential
\item[-] information
\\inform sb $\left\{
\begin{array}{@{}l@{}}
\text{of sth} \\
\text{that} \\
\text{to do}
\end{array}
\right.$
\\keep sb informed of sth
\\informed \emph{adj.} 对$\cdots$知晓的；有学问的；见多识广的
\\informative \emph{adj.} 信息量大的，提供有用信息的
\item[-] initial
\item[-] initiative \emph{n.} 主动性，积极性
\\take the $\sim$ to do sth
\item[-] injury \phantom{a} injure \emph{vt.} \phantom{a} injured \emph{adj.}
\item[-] inner \phantom{a} inner voice 心声
\item[-] innocent {\small 无辜的，无罪的，天真无邪的}
\\innocence
\item[-] innovation \phantom{a} innovate innovative
\item[-] input \phantom{a} output
\item[-] inquire
\\inquire about
\\inquiry
\item[-] insect
\item[-] inside
\item[-] insight
\\have a deep insight into
\item[-] insist \phantom{a} insist on = stick to
\\坚持；坚持认为，坚持要求（-main (should) do）
\\I insisted that I hadn\textquoteright t stolen the car.
\item[-] inspection 审视，检查，视察 \phantom{a} inspect
\item[-] inspire \phantom{a} inspiration -ed -ing
\item[-] instance \phantom{a} for instance
\item[-] instant
\\instant coffee / noodle
\\the instant = as soon as
\item[-] instead
\item[-] institude 研究所，学院
\item[-] institution 机构，团体
\item[-] instruction
\\instruct 指导，教导
\\instructions 说明书，指南
\item[-] instrument 乐器，器械
\item[-] insurance
\item[-] integrate
\\incorporate
\\integrate A into/with B
\\combine A and/with B
\item[-] integrity
\item[-] intelligent
\item[-] intend \phantom{a} intention
\\\begin{tabular}{@{} r | @{\hspace{0.1em}} l @{ } l @{}}
\multicolumn{1}{@{} r}{be} & intended & $\overset{\text{\small 针对}}{\text{for}}$ / $\overset{\text{\small 旨在}}{\text{to do}}$
\\& designed & for / to do
\\& aimed & at / to do
\\& targeted & at
\\& directed & at
\end{tabular}
\item[-] intense 强烈的，激烈的
\\intensity intensify
\item[-] intention
\item[-] interaction
\\interact with sb
\item[-] interest
\\\textcircled{1} 兴趣 have an $\sim$ in
\\\textcircled{2} 利息，利益，好处
\item[-] interesting
\item[-] internal
\item[-] international
\item[-] Internet
\item[-] interpret
\\interpretation interpreter
\item[-] interrupt
\item[-] intervention 干预，介入，调停
\item[-] interview \phantom{a} -er -ee
\item[-] into
\item[-] introduce
\item[-] introduction
\item[-] invent
\item[-] invention
\item[-] investigate
\\$\sim$ into
\\conduct an investigation into
\item[-] invest
\\n. investment
\item[-] invite
\\inviting
\\invitation (to)
\item[-] involve \phantom{a} involvement
\\\textcircled{1} involve oneself in \phantom{a} be involved in
\\\textcircled{2} $\sim$ sth / doing 包含，包括
\\\textcircled{3} 涉及到，牵扯到
\item[-] iron \emph{n.} 铁 \emph{v.}
\item[-] island
\item[-] issue
\\\emph{n.} \textcircled{1} 议题 \textcircled{2} 问题 \textcircled{3} 发行，发布
\\\phantom{aaa} be at issue 是问题焦点
\\\emph{vt.} \textcircled{1} 出版，发行刊物 \\\phantom{\emph{vt.}} issue a monthly newsletter
\\\phantom{\emph{vt}} \textcircled{2} 发行 \\\phantom{\emph{vt}} release/$\sim$ currency/a new album
\\\phantom{\emph{vt}} \textcircled{3} 公布，宣布，发出 \\\phantom{\emph{vt}} \mbox{$\sim$/announce a new policy/statement}
\item[-] it
\item[-] item 项目；条款；物品；商品
\item[-] its
\item[-] itself
\item[-] irrigate \phantom{a} irrigation
\item[-] immigrate to/into 迁徙，移民
\\immigration immigrant
\item[-] ink \phantom{a} in ink / English / a word
\item[-] insert
\item[-] insure / ensure
\\insurance company
\item[-] interval \emph{n.} 间隔，间隙，中场休息
\\These apple trees were planted at intervals / an interval.
\\at intervals
\\at an interval of + [time / place]
\item[-] ingredient
\end{itemize}
\end{multicols}
\end{document}