\chapter{词汇}
本章用来记录词汇的运用，如单词、词组等。未必符合字典序。
\section{A}
\raggedcolumns
\begin{multicols}{2}
\begin{itemize}
\item[-] a (an)
\item[-] abandon
\\\emph{n.} abandonment
\\abandon oneself to sth/doing
\\{\color{violet}desert}
\item[-] ability
\item[-] able
\item[-] abnormal
\item[-] aboard \emph{adv./prep.}
\\{\color{violet}board a plane}
\item[-] about
\\was / were about to do sth when \mbox{-main} did
\item[-] above
\\\emph{opp.} below
\item[-] abroad
\\{\color{violet}broaden one{\textquoteright}s horizons}
\item[-] absence
\\absence of mind 心不在焉
\\ in the absence / presence of
\item[-] absent
\\\begin{tabular}{@{} r | @{\hspace{0.1em}} l @{}}
be& absent from
\\& present at
\end{tabular}
\\absent-minded \emph{adj.}
\item[-] absolutely
\item[-] absorb
\\absorb A into B 把 A 并入 B
\\be absorbed in
\\\emph{n.} absorption
\\\emph{adj.} absorbing 引人入胜的
\item[-] abstract
\item[-] abuse
\item[-] academic
\\academic performance
\\academy \emph{n.} 研究所，学院
\item[-] accent
\\{\color{violet}dialect \emph{n.} 方言}
\item[-] accept
\\acceptance \emph{n.}
\\acceptable \emph{adj.}
\item[-] access
\\have access to sth
\\sth be accessible to sb
\\\phantom{sth be }{$\downarrow$\scriptsize 可达的；易懂的；平易近人的；可使用的}
\item[-] accident
\\by accident = accidentally
\item[-] accommadation
\\accommadate \emph{v.} \textcircled{1}给\ldots 提供膳宿\textcircled{2}容纳
\item[-] accompany
\\be accompanied by / with
\\keep sb company
\\in sb\textquoteright s company
\\in company with
\item[-] according to
= based on
\item[-] account
\\accountant
\\account for \textcircled{1}解释\textcircled{2}占比
\\give a vivid account of
\\take sth into account
\\an account of
\\on no account
\\open a bank account
\item[-] accurate
\\\emph{n.} accuracy
\item[-] accuse
\\accuse sb of = charge sb with
\item[-] ache
\\an aching leg
\item[-] achieve
\\accomplish / fulfill
\item[-] achivement
\\= accomplishment
\\a sense of $\sim$
\item[-] acid
\\acid rain
\item[-] acknowledge
\\-ment
\\$\sim$ doing
\\It is universally $\sim$ed that
\item[-] acquire
\\$\sim$ a good knowledge of
\\\emph{n.} acquisition
\item[-] across
\item[-] act
\\an act of kindness
\item[-] action
\\take action to do
\item[-] (in)active
\item[-] activity
\item[-] actor
\item[-] actress
\item[-] actually
\item[-] AD 公元
\\BC 公元前
\item[-] adapt
\\adapt oneself to 适应
\\be adapted for / from 改编
\\adaptable \emph{adj.}
\item[-] adaptation
\item[-] add
\\add A to B 把 A 加到 B
\\add to 增加，增添
\\add up to 合计
\\add up 把$\cdots$加起来
\\He added that\ldots
\\\emph{n.} addition in addition (to)
\\\emph{adv.} additionally
\item[-] addict （人）
\\be addicted to sth / doing
\\addictive \emph{adj.} 使人上瘾的
\item[-] addiction
\item[-] address
\\\emph{vt.} \textcircled{1}address sth 在$\cdots$上写收信人姓名地址 The letter was correctly addressed but was delivered to the wrong place.
\\\textcircled{2}address a meeting 在会议上发表演说
\\\textcircled{3}address a problem 解决
\\wrestle / cope with
\\handle / approach / fix
\\\textcircled{4}向$\cdots$说话 I was surprised that he addressed me in English.
\item[-] adjust
\\adjust (oneself) to
\\adjustable
\\\begin{tabular}{@{} r | @{\hspace{0.1em}} l @{}}
make& an adjustment to
\\& adjustments
\end{tabular}
\item[-] administration
\item[-] admire
\\$\sim$ sb for sth
\\admirable
\\in admiration
\item[-] admit
\\admit doing 承认
\\admit sb to / into sp. 允许进入（录取，录用）
\\admission {\color{violet}permission submission}
\item[-] adopt
\\adoption
\item[-] adorable
\\adore doing
\\adoration
\\have an affection for
\item[-] adult
\\ripe \emph{adj.}（瓜果）\phantom{a}(im)mature$\rightarrow$maturity
\item[-] advance
\\\emph{vi.} \textcircled{1}游行示威\textcircled{2}前进，行进
\\\emph{vt.} \textcircled{1}发展，使进步\textcircled{2}促进，推动\textcircled{3}把$\cdots$提前
\\in advance
\\advance \emph{adj.} 先进的
\item[-] advantage
\\A have an advantage over B in C
\\(dis)advantageous \emph{adj.} 有利的，优势的\phantom{a}{\color{violet}courageous}
\item[-] adventure
\\adventurous
\item[-] advertise \emph{v.}
\\advertising \emph{n.} 广告业
\\advertiser \emph{n.} 广告者
\item[-] advertisement (ad)
\item[-] advice
\item[-] advise
\\\begin{tabular}{@{} r @{}}
$\sim$/suggest/recommend$\left\{
\begin{array}{@{}l@{}}
\text{that \mbox{-main} (should) do} \\
\text{doing}
\end{array}
\right.$
\end{tabular}
\\advise / recommend sb to do
\\suggest sb doing
\item[-] advocate
\\\emph{v.} advocate doing
\\\emph{n.} 提倡者，主张者 an $\sim$ of
\item[-] affair
\item[-] affect
\\be affected by 影响；打动，感染
\\be affected with 感染（疾病）
\\{\color{violet}have an affection for = have a fancy for}
\item[-] afford
\\afford to do
\\affordable
\\affordability
\item[-] afraid
\\be $\sim$ of / to do
\item[-] Africa
\item[-] African
\item[-] after
\item[-] afternoon
\item[-] afterward
\item[-] again
\item[-] against
\\\begin{tabular}{@{} r | @{\hspace{0.1em}} l @{}}
反对 & 支持
\\be against& for
\\& in favor of
\end{tabular}
\item[-] age
\\\emph{vi.} 变老，老年化 ageing society / process
\\at the age of
\\aged + 年龄：后置定语
\item[-] agency 代理商
\\ agent 代理人
\\travel agency
\item[-] agenda
\item[-] ago
\\I lived in China 3 years ago.
\\I had lived in China 3 years before.
\item[-] agree
\\agree with sb
\\agree on 就$\cdots$达成共识
\\agreeable
\item[-] agreement
\item[-] agriculture
\\agricultural
\item[-] ahead
\\ahead of time = in advance
\item[-] aid
\\first aid 急救
\item[-] aim
\\aim to do 目的做
\\be aimd at 旨在，针对$\cdots$
\\be intended / designed for sb / to do
\item[-] air
\item[-] airline
\item[-] airport
\item[-] alarm
\\alarmed alarming
\item[-] alcohol 酒精
\\alcoholic \emph{n.} 酗酒者 \emph{adj.} 含酒精的
\item[-] alive 仅表语
\\sth come alive 变活跃，热闹
\\living 活着的 live 现场直播的
\item[-] all
\item[-] allow
\\$\sim$ sb to do
\\allow for 考虑到，顾及到
\item[-] almost
\item[-] alone
\item[-] along
\item[-] alongside
\item[-] aloud
\item[-] already
\item[-] also
\item[-] alternative
\\\begin{tabular}{@{} r | @{\hspace{0.1em}} l @{}}
have no & $\sim$ but to do
\\& option
\\& choice
\end{tabular}
\item[-] although
\item[-] altogether
\item[-] always
\item[-] a.m.
\item[-] amateur
\\\emph{opp.} professional
\item[-] amazing
\item[-] ambition
\item[-] ambitious
\item[-] ambulance
\item[-] America
\item[-] American
\item[-] among
\item[-] amount
\\{\small amount to = add up to = come to 总计}
\\{\small a large amount of = large amounts of [U]}
\item[-] amuse
\\amused amusing
\item[-] analyse (analyze)
\\analysis \emph{n.} give an analysis of
\item[-] ancestor
\item[-] ancient
\item[-] and
\item[-] anger
\item[-] angle 角 \phantom{a}{\color{violet}angel \emph{n.} 天使}
\item[-] angry
\item[-] animal
\item[-] ankle 脚踝
\item[-] announce
\\announcement
\\It is announced that\ldots
\item[-] annoy
\\annoyance annoyed annoying
\item[-] annual
\item[-] another
\item[-] answer
\\answer to a question
\\answer the door / telephone
\\anwser for\ldots 对$\cdots$承担后果
\item[-] ant
\item[-] anticipate
\\anticipation
\\It is anticipated that\ldots
\item[-] antique
\item[-] anxiety 焦虑；渴望
\item[-] anxious
\\be anxious $\underset{\text{\normalsize 渴望}}{\text{for}} / \underset{\text{\normalsize 担心}}{\text{ about}}$
\item[-] any
\item[-] anybody
\item[-] anyhow
\\{\color{violet}somehow \emph{adv.}\textcircled{1}不知怎么搞的，莫名其妙的\textcircled{2}以某种方式}
\item[-] anyone
\item[-] anything
\item[-] anyway
\item[-] anywhere
\item[-] apart
\\$\underset{\text{\normalsize (tore, torn)}}{\text{tear}}$ sth apart
\\take sth apart
\\set A apart from B 使 A 有别于 B，脱颖而出
\\= distinguish A from B
\item[-] apartment
\\flat
\item[-] apologise (apologize)
\\apology
\\apologise to sb for sth
\\owe / make an apology to sb for sth
\item[-] apparently
\\= obviously / clearly / evidently
\item[-] appeal
\\appeal to sb 吸引
\\appeal to sb to do / for sth 呼吁，恳求
\\apealing \emph{adj.}
\item[-] appear
\\= emerge
\\appearance
\\It appears / seems that
\item[-] appetite
\\have an appetite for
\item[-] applaud
\\thunderous applause come in waves
\item[-] apple
\item[-] applicant
\\apply to A for B 申请
\\apply A to B 应用
\\apply oneself to doing 致力于
\item[-] application
\item[-] apply
\item[-] appointment
\\appoint 约定，安排，任命，委任
\\make an appointment with sb
\\appoint + 地 / 时
\\the appointed place / time
\item[-] appreciate
\\\textcircled{1}欣赏，赏识，重视
\\\textcircled{2}感激 $\sim$ to doing
\\\phantom{\textcircled{2}感激 }I would $\sim$ it if you could\ldots
\\\textcircled{3}领会，理解，意识到
\\be appreciative of 感激
\\appreciation
\item[-] approach
\\\emph{n.}\textcircled{1}通道，入口\textcircled{2}方法，方式 $\sim$ to doing%
\textcircled{3}逼近，即将到来 with the $\sim$ of
\\\emph{v.}\textcircled{1}接近\textcircled{2}解决 $\sim$ a problem
\item[-] (in)appropriate
\\be $\sim$ for / to
\item[-] approve \emph{vt.} 批准，通过
\\(dis)approve of 赞成
\\(dis)approval \emph{n.}
\item[-] April
\item[-] arch
\item[-] architect
\\architecture
\item[-] area
\item[-] argue
\\\textcircled{1}争吵
\\\textcircled{2}说服 \begin{tabular}{@{} r | @{\hspace{0.1em}} l @{} | @{\hspace{0.1em}} l @{}}
& $\sim$\phantom{a} sb \phantom{a} & into \phantom{a} doing
\\& talk & out of
\end{tabular}
\\argument
\item[-] arise (arose, arisen) 出现，发生
\\{\small A arise / result from B = B result in A B 导致 A}
\item[-] arm
\\be armed / equipped with
\item[-] army
\item[-] around
\item[-] arrangement
\\make an arrangement for
\\arrange for sb to do sth
\\arrange sth for sb
\item[-] arrest
\item[-] arrive at / in
\\arrival
\item[-] arrow
\item[-] art
\\artistic
\item[-] article
\item[-] artist
\item[-] as
\item[-] ashamed
\\be ashamed of
\\shameful \emph{adj.} 令人羞耻的
\item[-] Asia
\item[-] Asian
\item[-] aside
\\set / lay / put aside
\\\textcircled{1}把$\cdots$放一边置之不理%
\\\textcircled{2}存钱，储蓄
\\set aside some time to do sth
\item[-] ask
\\ask sb for sth
\item[-] asleep 仅表语
\item[-] aspect
\\in all aspects
\item[-] assess
\\assessment self-assessment
\item[-] assign 分配，布置，指派，确定时间地点
\\assignment \emph{n.} 作业
\item[-] assistant
\item[-] association 协会；联系
\\associate with sb 和$\cdots$打交道
\\be associated with 和$\cdots$有关联
\item[-] assume
\\\textcircled{1} 认为，猜想
\\\textcircled{2} 承担（责任） $\sim$ responsibility for
\\\textcircled{3} 就职 $\sim$ office
\\$\underset{\text{\emph{conj.}}}{\text{Assuming}}$ that\ldots 倘若，假使
\item[-] assumption
\item[-] astonish
\item[-] astronaut
\item[-] astronomer
\\astronomy
\item[-] at
\item[-] athelete
\\athletic 强壮的，爱运动的
\item[-] Atlantic
\item[-] atmosphere
\item[-] attach
\\attach A to B 固定，贴，附
\\be attached to \textcircled{1}依恋，爱恋\textcircled{2}附属于\textcircled{3}有关联
\\attachment
\item[-] attack
\item[-] attain
\item[-] attempt
\\$\sim$ to do
\\in an attempt tp do 试图，企图，尝试
\item[-] attend
\\\textcircled{1}出席，参加
\\\textcircled{2}照料，处理（$\sim$ to）
\\\textcircled{3}上学
\begin{tabular}{@{} r | @{\hspace{0.1em}} l @{}}
$\sim$ & class
\\& school
\\& university
\end{tabular}
\\attendance
\item[-] attention
\\pay attention to
\\fix / concentrate / focus one\textquoteright s $\sim$ on
\item[-] attitude to / towards
\item[-] attract
\\attractive attraction
\item[-] audience
\item[-] August
\item[-] aunt
\item[-] Australia
\item[-] Australian
\item[-] author
\item[-] authority
\item[-] automatic
\item[-] autonomous
\item[-] autumn
\item[-] available
\\be $\sim$ to
\\availability
\item[-] average 平均的，普通的
\\on $\sim$
\item[-] avoid
\\$\sim$ doing
\\avoidance avoidable
\item[-] awake (awoke, awoken)
\\\emph{vt.} 唤起，唤醒 wake up
\\\emph{adj.} [表]醒着的
\item[-] award
\\\emph{n.} 奖
\\\emph{vt.} 颁发，授予
\item[-] aware
\\be $\sim$ of
\\arouse one\textquoteright s awareness of
\item[-] away
\item[-] awesome
\item[-] awful
\item[-] awkward 笨拙的；尴尬的
\item[-] abolish
\item[-] absurd
\\ridiculous
\item[-] abundant
\\be $\sim$ in = abound in
\item[-] abrupt
\item[-] accelerate
\\speed up
\item[-] accomplish
\item[-] accumulate
\item[-] acute
\item[-] accustomed
\\be $\sim$ to doing
\item[-] acquaintance
\\make one\textquoteright s $\sim$ / make the $\sim$ of sb
\item[-] adolescence 青春期，青春
\item[-] adolescent 青少年；青春期的
\item[-] adequate
\\\textcircled{1} 胜任
\\\begin{tabular}{@{} r | @{\hspace{0.1em}} l @{}}
be & $\sim$ \phantom{a} to doing
\\& equal
\\& up
\end{tabular}
\\be qualified for / to do
\\\textcircled{2} 足够的 be $\sim$ for
\item[-] aggressive
\item[-] allergic be $\sim$ to
\item[-] alley
\item[-] allocate
\item[-] allowance
\item[-] alphabet
\item[-] altitude
\item[-] ambassador
\item[-] ambassadress
\item[-] anchor \emph{n.} 锚 \emph{vi.} 停泊，泊船
\item[-] anecdote
\item[-] anniversary
\item[-] Antarctic 南极，南极地区
\\Antarctica 南极洲
\item[-] approximately = roughly
\item[-] apron
\item[-] arbitary
\item[-] ample sufficient
\item[-] Arctic 北极
\item[-] arithmetic 算术
\\algebra 代数 geometry 几何
\item[-] atom
\item[-] authentic
\item[-] avenue
\item[-] AI (artificial intelligence)
\item[-] alert
\item[-] app
\end{itemize}
\end{multicols}
\section{B}
\raggedcolumns
\begin{multicols}{2}
\begin{itemize}
\item[-] baby
\item[-] back \emph{v.} 支持，支援，支柱
\\back off 离开，后退
\item[-] background
\item[-] backward
\item[-] bacon
\item[-] bad
\\be bad / good for
\\be harmful / beneficial to
\\do harm to
\item[-] badminton
\item[-] bag
\item[-] bakery
\\bake \emph{v.} baker \emph{n.}
\item[-] balance
\\balanced
\item[-] ball
\item[-] ballet
\item[-] balloon
\\\emph{n.} 气球
\\\emph{v.} 膨胀，肿胀，激增
\item[-] bamboo
\item[-] ban (banned)
\\ban sb from doing
\\put a ban on
\item[-] banana
\item[-] band
\item[-] bank
\item[-] bar
\item[-] barbeque
\item[-] barely
\item[-] bark
\item[-] barrier
\item[-] base
\\base A on B
\\A be based on B
\\based on
\item[-] baseball
\item[-] basic
\\basically
\item[-] basin
\item[-] basis
\\on the basis of
\item[-] basket
\item[-] basketball
\item[-] bat 拍；蝙蝠
\item[-] bath
\\\emph{n.} take a bath
\\bathe \emph{v.} be bathed in
\item[-] bathroom
\item[-] battery
\item[-] battle
\item[-] bay
\item[-] BC
\item[-] be (am, are, is)
\item[-] beach
\item[-] bean
\item[-] bean curd (tofu)
\item[-] bear
\\\emph{n.} give sb a bear hug
\\\emph{v.}(bore, borne / born*)
\\\textcircled{1} 忍受，容忍 
\\\begin{tabular}{@{} c @{\hspace{0.1em}} l @{}}
bear & doing
\\stand &
\\tolerate &
\\put up with &
\end{tabular}
\\\textcircled{2} 经受得住 The ice can\textquoteright t bear your weight.
\\\textcircled{3} 携带
\\\textcircled{4} 结果实，生育*（过去分词 born 仅用于出生）He was born yesterday.
\item[-] beard
\item[-] beat (beat, beaten)
\\\textcircled{1} defeat
\\\textcircled{2} 心脏/脉搏的跳动
\\\textcircled{3} 有规律地击打 beat a drum
\\The rain beat against the windows.
\item[-] beautiful
\\beautify \emph{vt.} 美化
\\{\color{violet}purify \emph{vt.} 纯化 simplify \emph{vt.} 简化}
\item[-] beauty
\item[-] because
\item[-] become (became, become)
\item[-] bed
\item[-] bedroom
\item[-] beef
\item[-] beer
\item[-] before
\item[-] begin (began, begun)
\item[-] behalf
\\on behalf of / on one\textquoteright s behalf
\\representing\ldots
\item[-] behave
\\behave oneself
\\well-behaved
\item[-] behaviour (behavior)
\item[-] behind
\item[-] being
\\well-being human-being(s)
\item[-] belief
\\I have a firm belief that\ldots
\item[-] believe
\\believe in
\item[-] bell
\item[-] belong
\\A belong to B
\\belongings \emph{n.}
\\a sense of belonging
\item[-] below
\item[-] belt
\\safety belt \phantom{a} fasten your safety belt
\item[-] bend (bent, bent)
\\bend over
\\bend oneself to sth / doing 专心于
\item[-] beneath
\item[-] benefit
\\\begin{tabular}{@{} r | @{\hspace{0.1em}} l @{}}
be & beneficial to
\\& of benefit
\end{tabular}
\item[-] beside
\\next to
\item[-] besides
\item[-] best
\\make the best of
\item[-] bet
\\I can bet.
\item[-] better
\item[-] between
\item[-] beyond
\\beyond words / imagination / $\cdots$
\item[-] big
\item[-] bike (bicycle)
\item[-] bill \emph{n.} 账单，纸币，钞票，清单
\item[-] billion
\item[-] biology
\\biologist biological
\item[-] bird
\item[-] birth
\\bear
\\give birth to
\item[-] birthday
\item[-] biscuit
\item[-] bit
\\a bit (of) water
\item[-] bite (bit, bitten)
\\take a bite of {\color{violet}have a taste of}
\item[-] bitter
\item[-] black
\item[-] blackboard
\item[-] blame
\\\textcircled{1}blame sth on sb 归咎于
\\\phantom{\textcircled{1}}owe sth to sb 归功于
\\\textcircled{2}be to blame for 责备
\\\textcircled{3}be to blame for 理应受责备
\\\textcircled{4}take the blame for
\item[-] blank
\\go blank
\item[-] balnket
\item[-] bleed (bled, bled) bleeding
\item[-] bless
\\God bless us.
\\blessing \emph{n.} 祝福，恩宠，幸事
\item[-] blind
\\turn a blind eye to
\\turn a deaf ear to
\item[-] block
\\\emph{v.} 阻挡，阻塞，封锁 a blocked nose
\\\emph{n.} 木块；街区；大厦，大楼；障碍
\item[-] blog
\item[-] blood
\item[-] blouse
\item[-] blow
\\blow up a balloon 吹饱$\rightarrow$爆炸
\\blow out a candle
\\be a blow to 对$\cdots$是一个沉重打击
\item[-] blue \emph{adj.} 忧郁的，沮丧的
\item[-] board
\item[-] boat
\\by boat
\item[-] body
\item[-] boil
\item[-] bomb
\\The bomb exploded.
\item[-] bond
\\form a bond with
\\strengthen the $\sim$ between A and B
\item[-] bone \phantom{a} bony
\item[-] bonus
\item[-] book
\item[-] boost
\item[-] boot
\item[-] border
\item[-] bored
\\bore \emph{vt.} boredom \emph{n.}
\\be bored with
\\be tired of
\\be fed up with
\item[-] boring
\item[-] born
\item[-] borrow
\item[-] boss
\item[-] botanical \phantom{a} botany botanist
\item[-] both
\\not \ldots{} all/both/every/\ldots 部分否定
\item[-] bother
\\bother sb
\\\begin{tabular}{@{} r | @{\hspace{0.1em}} l @{}}
Don\textquoteright t bother & to do
\\& doing
\end{tabular}
\item[-] bottle
\item[-] bottom
\item[-] bounce
\\bounce a basketball
\item[-] bound
\\be bound to do
\item[-] boundary
\item[-] bow
\\bow to sb
\item[-] bowl
\item[-] bowling
\item[-] box
\item[-] boxing
\item[-] boy
\item[-] brain
\item[-] branch 树枝；分支；子公司；分店
\\tree branches
\item[-] brave
\\bravery
\\{\color{violet}courage courageous}
\item[-] bread
\item[-] break
\item[-] breakfast
\item[-] breast
\item[-] breath
\\breathless 气喘吁吁的；呼吸急促的
\\take a deep breath
\\hold one\textquoteright s breath
\\out of breath, \ldots
\item[-] breathe
\\breathe a sigh of relief
\\breathe in / out
\item[-] brick
\item[-] bride / bridegroom
\\bridal \emph{adj.} 新娘的，婚礼的
\item[-] bridge
\\bridge the gap between A and B
\item[-] brief
\\In brief / To be brief / Briefly speaking, \ldots
\\brief sb about sth 简单介绍
\item[-] bright
\\brighten my day / future
\item[-] brilliant
\item[-] bring (brought, brought)
\item[-] Britain
\item[-] British
\item[-] broad \phantom{a} broaden
\item[-] broadcast ($\sim$ed/$\sim$, $\sim$ed/$\sim$)
\\\emph{n.} 电视节目，广播节目
\\\emph{v.} 广播，播送，传播信息 The concert will be $\sim$ed live.
\item[-] brochure
\item[-] brother
\item[-] brown
\item[-] brush
\item[-] budget
\\on a tight budget
\item[-] buffet
\item[-] build
\item[-] building
\item[-] bunch 串，束，扎
\\a bunch of keys / flowers
\item[-] burn
\\have a burning desire to do
\\with a buring desire
\item[-] bury
\\bury oneself in
\\be buried in
\item[-] bus
\item[-] business 生意；公司；事情
\\It\textquoteright s none of your business.
\item[-] busy
\\busy / occupy onnself in doing / with sth
\\be busy / occupied
\item[-] but
\item[-] butcher
\item[-] butter
\item[-] button
\\\emph{n.} 按钮；纽扣
\\\emph{v.} 系纽扣，扣住 Please button your coat.
\item[-] buy (bought, bought)
\\purchase \phantom{a} make a purchase
\item[-] by
\item[-] bachelor
\item[-] bacterium (\emph{pl.} bacteria)
\item[-] baggage \phantom{a} luggage
\item[-] balcony
\item[-] bandage
\item[-] barber \phantom{a} barbershop
\item[-] bargain
\\\emph{vi.} $\sim$ with sb about sth
\\\emph{n.} 便宜货
\item[-] basement
\item[-] beg \phantom{a} beggar
\item[-] belly
\item[-] bench
\item[-] betray 背叛；泄露
\item[-] bid (bid, bid)
\\\textcircled{1}出价格\textcircled{2}投标\textcircled{3}命令，吩咐
\\\textcircled{4}\begin{tabular}{@{} r | @{\hspace{0.1em}} l @{}}
bid & goodbye \phantom{aaa} to sb
\\& good night / moring
\end{tabular}
\item[-] biography
\item[-] booth \phantom{a} stand
\item[-] boycott \emph{v.} 抵制，拒绝参加
\item[-] brake \emph{v./n.} 刹车；车闸
\item[-] brand \emph{n.} 品牌，商标，牌子
\\brand-new \emph{adj.} 崭新的
\item[-] broom
\item[-] brewary
\item[-] bungalow
\item[-] breakthrough
\\make a (huge) $\sim$ in
\item[-] burden \emph{vt.} 使有负担 / 重担
\\be burdened with
\item[-] burglar 盗贼
\\thief 小偷
\item[-] butterfly
\item[-] burst (burst, burst)
\\\emph{vt./vi.} { \small
\\\textcircled{1}爆裂，破裂，胀开
\\ My stomach will $\sim$.
\\ The balloon will $\sim$ if you blow it up any more.
\\ The dam $\sim$ under the weight of water.
\\ He felt he would $\sim$ with anger and shame.
\\\textcircled{2}闯入，破门而入 burst/break into sp
\\\textcircled{3}突然$\cdots$ 
\begin{tabular}{@{} r | @{\hspace{0.1em}} l @{}}
burst & into sth
\\& out doing
\end{tabular}
\\\textcircled{4}充满着
\\be bursting with passion/enthusiasm/\ldots
\\The road is $\sim$ing with cars.
\\\emph{n.} \textcircled{1}裂口，爆裂
\\\textcircled{2}（感情）迸发，（事情）突发
\\a burst of passion/\ldots
}
\item[-] bee
\item[-] bias
\item[-] bin
\item[-] bug
\item[-] bully
\end{itemize}
\end{multicols}
\section{C}
\raggedcolumns
\begin{multicols}{2}
\begin{itemize}
\item[-] cabbage
\item[-] caf\'e
\item[-] cafeteria
\item[-] cage
\item[-] cake
\item[-] calculate
\item[-] calendar
\item[-] call
\item[-] calligraphy
\item[-] calm
\item[-] calorie
\item[-] camel
\item[-] camera
\item[-] camp
\item[-] campaign
\item[-] campus
\item[-] can
\item[-] Canada
\item[-] Canadian
\item[-] canal
\item[-] cancel
\item[-] cancer
\item[-] candidate
\item[-] candlechildren
\item[-] candy
\item[-] canteen
\item[-] cap
\item[-] capable
\item[-] capacity
\item[-] capital
\item[-] capsule
\item[-] captain
\item[-] car
\item[-] carbon
\item[-] card
\item[-] care
\item[-] career
\item[-] careful
\item[-] careless
\item[-] carpet
\item[-] carrot
\item[-] carry
\item[-] cartoon
\item[-] carve
\item[-] case
\item[-] cash
\item[-] cast
\item[-] castle
\item[-] cat
\item[-] catch
\item[-] category
\item[-] cattle
\item[-] cause
\item[-] cave
\item[-] cease
\item[-] ceiling
\item[-] celebrate
\item[-] celebrity
\item[-] cell
\item[-] cent
\item[-] centimetre (centimeter)
\item[-] central
\item[-] centre (center)
\item[-] century
\item[-] certain
\item[-] certainly
\item[-] certificate
\item[-] chain
\item[-] chair
\item[-] chairman / chairwoman
\item[-] chalk
\item[-] challenge
\item[-] champion
\item[-] chance
\item[-] change
\item[-] channel
\item[-] chaos
\item[-] chapter
\item[-] character
\item[-] characteristc
\item[-] charge
\item[-] charity
\item[-] chart
\item[-] chat
\item[-] cheap
\item[-] cheat
\item[-] check
\item[-] cheek
\item[-] cheer
\item[-] cheese
\item[-] chef
\item[-] chemical
\item[-] chemist
\item[-] chemistry
\item[-] chess
\item[-] chest
\item[-] chew
\item[-] chicken
\item[-] chief
\item[-] child (\emph{pl.} children)
\item[-] China
\item[-] china
\item[-] Chinese
\item[-] chocolate
\item[-] choice
\item[-] choke
\item[-] choose
\item[-] chopsticks
\item[-] chorus
\item[-] Christmas
\item[-] church
\item[-] cigarette
\item[-] cinema
\item[-] circle
\item[-] circuit
\item[-] circumstance
\item[-] circus
\item[-] cite
\item[-] citizen
\item[-] city
\item[-] civil
\item[-] civilian
\item[-] civilisation (civilization)
\item[-] claim
\item[-] clap
\item[-] clarify
\item[-] class
\item[-] classic
\item[-] classmate
\item[-] classroom
\item[-] clay
\item[-] clean
\item[-] clear
\item[-] clerk
\item[-] clever
\item[-] click
\item[-] client
\item[-] climate
\item[-] climb
\item[-] clinic
\item[-] clock
\item[-] clone
\item[-] close
\item[-] cloth
\item[-] clothes
\item[-] cloud
\item[-] cloudy
\item[-] club
\item[-] clue
\item[-] coach
\item[-] coal
\item[-] coast
\item[-] coat
\item[-] coffee
\item[-] coin
\item[-] cold
\item[-] collapse
\item[-] collar
\item[-] collect
\item[-] collection
\item[-] college
\item[-] colour (color)
\item[-] column
\item[-] combine
\item[-] come
\item[-] comedy
\item[-] comfort
\item[-] comfortable
\item[-] comic
\item[-] comment
\item[-] commercial
\item[-] commit
\item[-] commitment
\item[-] committee
\item[-] common
\item[-] communicate
\item[-] communication
\item[-] communist
\item[-] community
\item[-] company
\item[-] compare
\item[-] comparison
\item[-] compete
\item[-] competence
\item[-] competition
\item[-] complain
\item[-] complete
\item[-] complex
\item[-] complicated
\item[-] component
\item[-] compose
\item[-] composition
\item[-] comprehension
\item[-] comprehensive
\item[-] comprise
\item[-] computer
\item[-] concentrate
\item[-] concept
\item[-] concern
\item[-] concert
\item[-] conclude
\item[-] conclusion
\item[-] concrete
\item[-] condition
\item[-] conduct
\item[-] conference
\item[-] confidence
\item[-] confirm
\item[-] conflict
\item[-] Confucianism
\item[-] Confucius
\item[-] confused
\item[-] congratulation
\item[-] connect
\item[-] consequence
\item[-] conservation
\item[-] consider
\item[-] consist
\item[-] consistent
\item[-] constant
\item[-] constitution
\item[-] construction
\item[-] consultant
\item[-] consultation
\item[-] consume
\item[-] consumption
\item[-] contact
\item[-] contain
\item[-] contemporary
\item[-] content
\item[-] contest
\item[-] context
\item[-] continent
\item[-] continue
\item[-] contract
\item[-] contradictory
\item[-] contrary
\item[-] contrast
\item[-] contribution
\item[-] control
\item[-] convenient
\item[-] conventional
\item[-] conversation
\item[-] convince
\item[-] cook
\item[-] cookie
\item[-] cool
\item[-] cooperate
\item[-] copy
\item[-] core
\item[-] corn
\item[-] corner
\item[-] corporate
\item[-] correct
\item[-] correspond
\item[-] cost
\item[-] costume
\item[-] cottage
\item[-] cotton
\item[-] cough
\item[-] could
\item[-] council
\item[-] count
\item[-] country
\item[-] countryside
\item[-] county
\item[-] couple
\item[-] courage
\item[-] course
\item[-] court
\item[-] cousin
\item[-] cover
\item[-] coverage
\item[-] cow
\item[-] crash
\item[-] crayon
\item[-] crazy
\item[-] cream
\item[-] create
\item[-] creative
\item[-] creature
\item[-] credit
\item[-] crew
\item[-] crime
\item[-] crisis
\item[-] criterion (\emph{pl.} criteria)
\item[-] critical
\item[-] criticise (criticize)
\item[-] crop
\item[-] cross
\item[-] crowd
\item[-] crucial
\item[-] cruel
\item[-] cry
\item[-] cuisine
\item[-] culture
\item[-] cup
\item[-] cupboard
\item[-] cure
\item[-] curious
\item[-] current
\item[-] curtain
\item[-] custom
\item[-] customer
\item[-] cut
\item[-] cute
\item[-] cycle
\item[-] caption
\item[-] carpenter
\item[-] carriage
\item[-] carrier
\item[-] cassette
\item[-] casual
\item[-] catastrophe
\item[-] cater
\item[-] caution
\item[-] ceremony
\item[-] chant
\item[-] chart
\item[-] choir
\item[-] circulate
\item[-] claw
\item[-] clumsy
\item[-] coincidence
\item[-] collision
\item[-] comb
\item[-] command
\item[-] companion
\item[-] compromise
\item[-] compulsory
\item[-] condemn
\item[-] confidential
\item[-] conscience
\item[-] consensus
\item[-] conservative
\item[-] controversial
\item[-] convey
\item[-] corrupt
\item[-] cosy (cozy)
\item[-] counter
\item[-] curriculum
\item[-] cushion
\item[-] cube
\item[-] cubic
\item[-] currency
\item[-] capture
\item[-] CE (Common Era)
\item[-] charm
\item[-] childhood
\item[-] chip
\item[-] chore
\item[-] collaborate
\item[-] compass
\item[-] consious
\item[-] craft
\item[-] cucumber
\item[-] curve
\end{itemize}
\end{multicols}
\section{D}
\raggedcolumns
\begin{multicols}{2}
\begin{itemize}
\item[-] daily
\item[-] damage
\item[-] damp
\item[-] dance
\item[-] danger
\item[-] dangerous
\item[-] dare
\item[-] dark
\item[-] data
\item[-] database
\item[-] date
\item[-] daughter
\item[-] day
\item[-] dead
\item[-] deadline
\item[-] deaf
\item[-] deal
\item[-] dear
\item[-] death
\item[-] debate
\item[-] debt
\item[-] decade
\item[-] December
\item[-] decent
\item[-] decide
\item[-] decision
\item[-] declare
\item[-] decline
\item[-] decorate
\item[-] decrease
\item[-] deep
\item[-] deer
\item[-] defeat
\item[-] defence (defense)
\item[-] defend
\item[-] definitely
\item[-] definition
\item[-] degree
\item[-] delay
\item[-] delete
\item[-] delicate
\item[-] delicious
\item[-] deliver
\item[-] demand
\item[-] demonstrate
\item[-] dentist
\item[-] deny
\item[-] department
\item[-] departure
\item[-] depend
\item[-] depress
\item[-] depth
\item[-] describe
\item[-] description
\item[-] desert
\item[-] deserve
\item[-] design
\item[-] desire
\item[-] desk
\item[-] desperate
\item[-] despite
\item[-] dessert
\item[-] destination
\item[-] destroy
\item[-] detail
\item[-] detect
\item[-] detective
\item[-] determine
\item[-] develop
\item[-] development
\item[-] device
\item[-] devote
\item[-] diagram
\item[-] dialogue (dialog)
\item[-] diamond
\item[-] diary
\item[-] dictionary
\item[-] die
\item[-] diet
\item[-] differ
\item[-] difference
\item[-] different
\item[-] difficult
\item[-] difficulty
\item[-] dig
\item[-] digest
\item[-] digital
\item[-] dignity
\item[-] dimension
\item[-] dining
\item[-] dinner
\item[-] dinosaur
\item[-] direct
\item[-] direction
\item[-] director
\item[-] directory
\item[-] dirty
\item[-] disability
\item[-] disabled
\item[-] disappear
\item[-] disappointed
\\disapoint
\item[-] disaster
\item[-] discipline
\item[-] discount
\item[-] discover
\item[-] discovery
\item[-] discrimination
\item[-] discuss
\item[-] discussion
\item[-] disease
\item[-] dish
\item[-] disk (disc)
\item[-] dismiss
\item[-] display
\item[-] distance
\item[-] distant
\item[-] distinct
\item[-] distinguish
\item[-] distribution
\item[-] district
\item[-] disturb
\item[-] dive
\item[-] diverse
\item[-] divide
\item[-] division
\item[-] dizzy
\item[-] do
\item[-] docter
\item[-] document
\item[-] dog
\item[-] dollar
\item[-] dolphin
\item[-] domain
\item[-] domestic
\item[-] dominate
\item[-] donate
\item[-] door
\item[-] dormitory
\item[-] double
\item[-] doubt
\item[-] down
\item[-] download
\item[-] downstairs
\item[-] downtown
\item[-] dozen
\item[-] draft
\item[-] drag
\item[-] dragon
\item[-] drama
\item[-] dramatic
\item[-] draw
\item[-] drawer
\item[-] dream
\item[-] dress
\item[-] drill
\item[-] drink
\item[-] drive
\item[-] driver
\item[-] drop
\item[-] drought
\item[-] drug
\item[-] dry
\item[-] duck
\item[-] due to
\item[-] dumpling
\item[-] duration
\item[-] during
\item[-] dust
\item[-] duty
\item[-] dynamic
\item[-] dynasty
\item[-] dash
\item[-] dawn
\item[-] delight
\item[-] deliberately
\item[-] deposit
\item[-] dial
\item[-] dilemma
\item[-] dioxide
\item[-] dip
\item[-] diploma
\item[-] discourage
\item[-] disgust
\item[-] divorce
\item[-] doll
\item[-] dot
\item[-] drawback
\item[-] dam
\item[-] dedicate
\item[-] drone
\item[-] drown
\end{itemize}
\end{multicols}
\section{E}
\raggedcolumns
\begin{multicols}{2}
\begin{itemize}
\item[-] each
\item[-] eager
\item[-] eagle
\item[-] ear
\item[-] early
\item[-] earn
\item[-] earth
\item[-] earthquake
\item[-] ease
\item[-] east
\item[-] eastern
\item[-] easy
\item[-] eat
\item[-] ecology
\item[-] economic
\\economy
\item[-] edge
\item[-] editor
\item[-] education
\item[-] educator
\item[-] effect
\item[-] efficient
\item[-] effort
\item[-] egg
\item[-] eight
\item[-] eighteen
\item[-] eighth
\item[-] eighty
\item[-] either
\item[-] elder
\item[-] elderly
\item[-] election
\item[-] electricity
\item[-] electronic
\item[-] elegant
\item[-] element
\item[-] elephant
\item[-] eleven
\item[-] else
\item[-] elsewhere
\item[-] email
\item[-] embarrassed
\item[-] emerge
\item[-] emergency
\item[-] emotion
\item[-] emperor
\item[-] emphasis
\item[-] employ
\item[-] empty
\item[-] enable
\item[-] encounter
\item[-] encourage
\item[-] end
\item[-] enemy
\item[-] energetic
\item[-] energy
\item[-] engage
\item[-] engine
\item[-] engineer
\item[-] England
\item[-] English
\item[-] enhance
\item[-] enjoy
\item[-] enormous
\item[-] enough
\item[-] ensure
\item[-] enter
\item[-] enterprise
\item[-] entertainment
\item[-] enthusiatic
\item[-] entirely
\item[-] entitle
\item[-] entrance
\item[-] entry
\item[-] envelope
\item[-] environment
\item[-] envy
\item[-] episode
\item[-] equal
\item[-] equator
\item[-] equipment
\item[-] era
\item[-] eraser
\item[-] error
\item[-] erupt
\item[-] escape
\item[-] especially
\item[-] essay
\item[-] essential
\item[-] establish
\item[-] estate
\item[-] estimate
\item[-] Europe
\item[-] European
\item[-] evaluate
\item[-] eve
\item[-] even
\item[-] evening
\item[-] event
\item[-] eventually
\item[-] ever
\item[-] every
\item[-] everybody
\item[-] everyday
\item[-] everyone
\item[-] everything
\item[-] everywhere
\item[-] evidence
\item[-] exactly
\item[-] exam (examination)
\item[-] examine
\item[-] example
\item[-] excellent
\item[-] except
\item[-] exceptional
\item[-] exchange
\item[-] excited
\item[-] exciting
\item[-] excuse
\item[-] exercise
\item[-] exhibition
\item[-] exist
\item[-] exit
\item[-] expand
\item[-] expansion
\item[-] expect
\item[-] expectation
\item[-] expense
\item[-] expensive
\item[-] experience
\item[-] experiment
\item[-] expert
\item[-] explain
\item[-] explode
\item[-] explore
\item[-] export
\item[-] expose
\item[-] exposure
\item[-] express
\item[-] extend
\item[-] extension
\item[-] extent
\item[-] external
\item[-] extinction
\item[-] extra
\item[-] extraordinary
\item[-] extremely
\item[-] eye
\item[-] embassador
\item[-] embassy
\item[-] edition
\item[-] enlarge
\item[-] enquire
\item[-] enquiry
\item[-] electric
\item[-] elevator
\item[-] eliminate
\item[-] empathy
\item[-] empress
\item[-] endangered
\item[-] ethical
\item[-] ethnic
\item[-] evolve
\item[-] exceed
\item[-] exhaust
\end{itemize}
\end{multicols}
\section{F}
\raggedcolumns
\begin{multicols}{2}
\begin{itemize}
\item[-] fabric
\item[-] face
\item[-] facilitate
\item[-] facility
\item[-] fact
\item[-] factor
\item[-] factory
\item[-] fail
\item[-] failure
\item[-] fair
\item[-] faith
\item[-] fall
\item[-] false
\item[-] familiar
\item[-] family
\item[-] famous
\item[-] fan
\item[-] fancy
\item[-] fantastic
\item[-] fantasy
\item[-] far
\item[-] farm
\item[-] farmer
\item[-] fashion
\item[-] fast
\item[-] fat
\item[-] father (dad)
\item[-] fault
\item[-] favour (favor)
\item[-] favourite (favorite)
\item[-] fear
\item[-] feature
\item[-] February
\item[-] fee
\item[-] feeling
\item[-] fellow
\item[-] female
\item[-] fence
\item[-] festival
\item[-] fetch
\item[-] fever
\item[-] few
\item[-] fibre (fiber)
\item[-] fiction
\item[-] field
\item[-] fifteen
\item[-] fifth
\item[-] fifty
\item[-] fight
\item[-] figure
\item[-] file
\item[-] fill
\item[-] film
\item[-] finally
\\final
\item[-] finance
\item[-] financial
\item[-] find
\item[-] finding
\item[-] fine
\item[-] finger
\item[-] finish
\item[-] fire
\item[-] firm
\item[-] first
\item[-] fish
\item[-] fisherman
\item[-] fist
\item[-] fit
\item[-] five
\item[-] fix
\item[-] flag
\item[-] flash
\item[-] flat
\item[-] flavour (flavor)
\item[-] flexible
\item[-] flight
\item[-] flood
\item[-] floor
\item[-] flour
\item[-] flow
\item[-] flower
\item[-] flu
\item[-] fluent
\item[-] fly
\item[-] focus
\item[-] foggy
\item[-] fold
\item[-] folk
\item[-] follow
\item[-] fond
\item[-] food
\item[-] foot (\emph{pl.} feet)
\item[-] football
\item[-] for
\item[-] force
\item[-] forecast
\item[-] forehead
\item[-] foreign
\item[-] forest
\item[-] forever
\item[-] forget
\item[-] forgive
\item[-] fork
\item[-] form
\item[-] formal
\item[-] format
\item[-] former
\item[-] fortunately
\item[-] forty
\item[-] forward
\item[-] found
\item[-] foundation
\item[-] fountain
\item[-] four
\item[-] fourteen
\item[-] fourth
\item[-] fox
\item[-] France
\item[-] frank
\item[-] free
\item[-] freedom
\item[-] freeze
\item[-] French
\item[-] frequency
\item[-] frequently
\item[-] fresh
\item[-] friction
\item[-] Friday
\item[-] fridge (refrigerator)
\item[-] friend
\item[-] friendly
\item[-] friendship
\item[-] frightened
\item[-] frog
\item[-] from
\item[-] front
\item[-] frontier
\item[-] frost
\item[-] fruit
\item[-] fry
\item[-] fuel
\item[-] full
\item[-] fun
\item[-] function
\item[-] fund
\item[-] fundamental
\item[-] funny
\item[-] furniture
\item[-] further
\item[-] future
\item[-] facial
\item[-] fade
\item[-] fare
\item[-] fasten
\item[-] fax
\item[-] feather
\item[-] feast
\item[-] federal
\item[-] ferry
\item[-] fierce
\item[-] firework
\item[-] flame
\item[-] flee
\item[-] flesh
\item[-] foolish
\item[-] forbid
\item[-] foresee
\item[-] fortnight
\item[-] foster
\item[-] fox
\item[-] fragile
\item[-] fragrant
\item[-] framework
\item[-] funeral
\item[-] fur
\item[-] furnished
\item[-] fable
\item[-] faint
\item[-] fascinating
\item[-] fertile
\item[-] fireman (\emph{pl.} firemen)
\item[-] float
\item[-] fog
\item[-] fool
\item[-] fortune
\item[-] frame
\item[-] fulfil(l)
\item[-] furthermore
\end{itemize}
\end{multicols}
\section{G}
\raggedcolumns
\begin{multicols}{2}
\begin{itemize}
\item[-] gain
\item[-] gallery
\item[-] game
\item[-] gap
\item[-] garbage
\item[-] garden
\item[-] garlic
\item[-] gas
\item[-] gate
\item[-] gather
\item[-] gender
\item[-] general
\item[-] generate
\item[-] generation
\item[-] generous
\item[-] genius
\item[-] gentle
\item[-] gentleman
\item[-] genuine
\item[-] geography
\item[-] geometry
\item[-] German
\item[-] Germany
\item[-] get
\item[-] gift
\item[-] gifted
\item[-] giraffe
\item[-] girl
\item[-] give
\item[-] glad
\item[-] glass
\item[-] global
\item[-] globe
\item[-] glove
\item[-] glue
\item[-] go
\item[-] goal
\item[-] goat
\item[-] gold
\item[-] golf
\item[-] good
\item[-] goodbye (bye)
\item[-] goods
\item[-] government
\item[-] grab
\item[-] grade
\item[-] gradually
\item[-] graduate
\item[-] grain
\item[-] grammar
\item[-] gramme (gram)
\item[-] grand
\item[-] granddaughter
\item[-] grandfather (grandpa)
\item[-] grandmother (grandma)
\item[-] grandparent
\item[-] grandson
\item[-] grape
\item[-] grasp
\item[-] grass
\item[-] grateful
\item[-] gravity
\item[-] great
\item[-] greedy
\item[-] green
\item[-] greenhouse
\item[-] greet
\item[-] grey
\item[-] grocery
\item[-] ground
\item[-] group
\item[-] grow
\item[-] guarantee
\item[-] guard
\item[-] guess
\item[-] guest
\item[-] guidance
\item[-] guide
\item[-] guideline
\item[-] guilty
\item[-] guitar
\item[-] gun
\item[-] guy
\item[-] gym
\item[-] gymnastics
\item[-] garage
\item[-] garment
\item[-] gesture
\item[-] glance
\item[-] glare
\item[-] glory
\item[-] gradual
\item[-] graph
\item[-] gene
\item[-] giant
\item[-] god
\item[-] graceful
\item[-] gratitude
\end{itemize}
\end{multicols}
\section{H}
\raggedcolumns
\begin{multicols}{2}
\begin{itemize}
\item[-] habit
\item[-] habitat
\item[-] hair
\item[-] half
\item[-] hall
\item[-] ham
\item[-] hamburger
\item[-] hand
\item[-] handbag
\item[-] handkerchief
\item[-] handle
\item[-] handsome
\item[-] handwriting
\item[-] hang
\item[-] happen
\item[-] happy
\item[-] hard
\item[-] hardly
\item[-] harm
\item[-] harmful
\item[-] harmonious
\item[-] harmony
\item[-] harvest
\item[-] hat
\item[-] hatch
\item[-] hate
\item[-] have (has)
\item[-] he
\item[-] head
\item[-] headache
\item[-] health
\item[-] healthy
\item[-] hear
\item[-] heart
\item[-] heat
\item[-] heavy
\item[-] height
\item[-] hello
\item[-] help
\item[-] helpful
\item[-] hen
\item[-] hence
\item[-] her
\item[-] herb
\item[-] here
\item[-] hero
\item[-] hers
\item[-] herself
\item[-] hesitate
\item[-] hi
\item[-] hide
\item[-] high
\item[-] highlight
\item[-] hike
\item[-] hill
\item[-] him
\item[-] himself
\item[-] hire
\item[-] his
\item[-] historic
\item[-] history
\item[-] hit
\item[-] hobby
\item[-] hold
\item[-] hole
\item[-] holiday
\item[-] home
\item[-] hometown
\item[-] homework
\item[-] honest
\item[-] honour (honor)
\item[-] hope
\item[-] horrible
\item[-] horse
\item[-] hospital
\item[-] host
\item[-] hot
\item[-] hotel
\item[-] hour
\item[-] house
\item[-] household
\item[-] housework
\item[-] housing
\item[-] how
\item[-] however
\item[-] hug
\item[-] huge
\item[-] human
\item[-] humble
\item[-] humorous
\item[-] hundred
\item[-] hungry
\item[-] hunt
\item[-] hurricane
\item[-] hurry
\item[-] hurt
\item[-] husband
\item[-] hydrogen
\item[-] hammer
\item[-] handful
\item[-] handy
\item[-] harbor
\item[-] hardship
\item[-] headline
\item[-] heel
\item[-] helicopter
\item[-] helmet
\item[-] hook
\item[-] howl
\item[-] heritage
\item[-] highway
\item[-] horror
\item[-] hostess
\item[-] humanity
\item[-] humour (humor)
\item[-] hybrid
\end{itemize}
\end{multicols}
\section{I}
\raggedcolumns
\begin{multicols}{2}
\begin{itemize}
\item[-] I
\item[-] ice
\item[-] ice-cream
\item[-] idea
\item[-] ideal
\item[-] identical
\item[-] identify
\item[-] identity
\item[-] idiom
\item[-] if
\item[-] ignore
\item[-] ill
\item[-] illegal
\item[-] illness
\item[-] illustrate
\item[-] image
\item[-] imagine
\item[-] immediately
\item[-] impact
\item[-] imply
\item[-] import
\item[-] important
\item[-] impossible
\item[-] impress
\item[-] impression
\item[-] improve
\item[-] in
\item[-] inch
\item[-] incident
\item[-] include
\item[-] income
\item[-] increase
\item[-] incredible
\item[-] indeed
\item[-] independent
\item[-] India
\item[-] Indian
\item[-] indicate
\item[-] individual
\item[-] industry
\item[-] infection
\item[-] infer
\item[-] influence
\item[-] influential
\item[-] information
\item[-] initial
\item[-] initiative
\item[-] injury
\item[-] inner
\item[-] innocent
\item[-] innovation
\item[-] input
\item[-] inquire
\item[-] insect
\item[-] inside
\item[-] insight
\item[-] insist
\item[-] inspection
\item[-] inspire
\item[-] instance
\item[-] instant
\item[-] instead
\item[-] institude
\item[-] institution
\item[-] instruction
\item[-] instrument
\item[-] insurance
\item[-] integrate
\item[-] integrity
\item[-] intelligent
\item[-] intend
\item[-] intense
\item[-] intention
\item[-] interaction
\item[-] interest
\item[-] interesting
\item[-] internal
\item[-] international
\item[-] Internet
\item[-] interpret
\item[-] interrupt
\item[-] intervention
\item[-] interview
\item[-] into
\item[-] introduce
\item[-] introduction
\item[-] invent
\item[-] invention
\item[-] investigate
\item[-] invest
\\n. investment
\item[-] invite
\item[-] involve
\item[-] iron
\item[-] island
\item[-] issue
\item[-] it
\item[-] item
\item[-] its
\item[-] itself
\item[-] irrigate
\item[-] immigrate
\item[-] ink
\item[-] insert
\item[-] insure / ensure
\item[-] interval
\item[-] ingredient
\end{itemize}
\end{multicols}
\section{J}
\raggedcolumns
\begin{multicols}{2}
\begin{itemize}
\item[-] jacket
\item[-] jam
\item[-] January
\item[-] Japan
\item[-] Japanese
\item[-] jaw
\item[-] jazz
\item[-] jeans
\item[-] job
\item[-] jog
\item[-] join
\item[-] joint
\item[-] joke
\item[-] journal
\item[-] journalist
\item[-] journey
\item[-] joy
\item[-] judge
\item[-] juice
\item[-] July
\item[-] jump
\item[-] June
\item[-] jungle
\item[-] junior
\item[-] just
\item[-] justice
\item[-] justify
\item[-] jar
\item[-] jet
\item[-] jeep
\item[-] jewellery (jewelry)
\end{itemize}
\end{multicols}
\section{K}
\raggedcolumns
\begin{multicols}{2}
\begin{itemize}
\item[-] kangaroo
\item[-] keep
\item[-] kettle
\item[-] key
\item[-] keyboard
\item[-] kick
\item[-] kid
\item[-] kill
\item[-] kilo (kilogramme, kilogram)
\item[-] kilometre (kilometer)
\item[-] kind
\item[-] kindergarten
\item[-] king
\item[-] kingdom
\item[-] kiss
\item[-] kit
\item[-] kitchen
\item[-] kite
\item[-] knee
\item[-] knife
\item[-] knock
\item[-] know
\item[-] knowledge
\item[-] keen
\item[-] kung fu
\end{itemize}
\end{multicols}
\section{L}
\raggedcolumns
\begin{multicols}{2}
\begin{itemize}
\item[-] lab (laboratory)
\item[-] label
\item[-] labour (labor)
\item[-] lack
\item[-] lady
\item[-] lake
\item[-] lamb
\item[-] lamp
\item[-] land
\item[-] landscape
\item[-] language
\item[-] lantern
\item[-] lap
\item[-] laptop
\item[-] large
\item[-] last
\item[-] late
\item[-] later
\item[-] laugh
\item[-] launch
\item[-] law
\item[-] lawyer
\item[-] lay
\item[-] lazy
\item[-] lead
\item[-] leader
\item[-] leadership
\item[-] leaf
\item[-] league
\item[-] leak
\item[-] learn
\item[-] least
\item[-] leather
\item[-] leave
\item[-] lecture
\item[-] left
\item[-] leg
\item[-] legal
\item[-] leisure
\item[-] lemon
\item[-] lend
\item[-] length
\item[-] less
\item[-] lesson
\item[-] let
\item[-] letter
\item[-] level
\item[-] liberation
\item[-] liberty
\item[-] librarian
\item[-] library
\item[-] license
\item[-] lie
\item[-] life
\item[-] lift
\item[-] light
\item[-] like
\item[-] likely
\item[-] limit
\item[-] limited
\item[-] line
\item[-] link
\item[-] lion
\item[-] liquid
\item[-] list
\item[-] listen
\item[-] literally
\item[-] literary
\item[-] literature
\item[-] litter
\item[-] little
\item[-] live
\item[-] lively
\item[-] living
\item[-] load
\item[-] loan
\item[-] local
\item[-] location
\item[-] lock
\item[-] log
\item[-] logical
\item[-] London
\item[-] lonely
\item[-] long
\item[-] look
\item[-] loose
\item[-] lose
\item[-] loss
\item[-] lot
\item[-] loud
\item[-] love
\item[-] lovely
\item[-] low
\item[-] lower
\item[-] luck
\item[-] lucky
\item[-] lunar
\item[-] lunch
\item[-] lung
\item[-] luxury
\item[-] latter
\item[-] laundry
\item[-] lid
\item[-] lightning
\item[-] lip
\item[-] loaf
\item[-] luggage
\item[-] lame
\item[-] lean
\item[-] leap
\item[-] legend
\item[-] lifestyle
\item[-] livestock
\item[-] lost
\item[-] loyal
\end{itemize}
\end{multicols}
\section{M}
\raggedcolumns
\begin{multicols}{2}
\begin{itemize}
\item[-] machine
\item[-] mad
\item[-] madam
\item[-] magazine
\item[-] magic
\item[-] mail
\item[-] main
\item[-] maintain
\item[-] major
\item[-] majority
\item[-] make
\item[-] male
\item[-] man (\emph{pl.} men)
\item[-] manage
\item[-] manager
\item[-] mankind
\item[-] manner
\item[-] many
\item[-] map
\item[-] marathon
\item[-] March
\item[-] march
\item[-] mark
\item[-] market
\item[-] marriage
\item[-] marry
\item[-] mass
\item[-] massive
\item[-] master
\item[-] match
\item[-] material
\item[-] maths (mathematics)
\item[-] matter
\item[-] mature
\item[-] maximum
\item[-] May
\item[-] may
\item[-] maybe
\item[-] me
\item[-] meal
\item[-] mean
\item[-] meaning
\item[-] means
\item[-] measure
\item[-] meat
\item[-] mechanic
\item[-] medal
\item[-] medical
\item[-] medicine
\item[-] medium (\emph{pl.} media)
\item[-] meet
\item[-] meeting
\item[-] member
\item[-] membership
\item[-] memorial
\item[-] memory
\item[-] mental
\item[-] mention
\item[-] menu
\item[-] mercy
\item[-] merely
\item[-] merry
\item[-] mess
\item[-] message
\item[-] metal
\item[-] method
\item[-] metre (meter)
\item[-] microscope
\item[-] middle
\item[-] midnight
\item[-] might
\item[-] mild
\item[-] mile
\item[-] military
\item[-] milk
\item[-] millimetre (millimeter)
\item[-] million
\item[-] mind
\item[-] mine
\item[-] mineral
\item[-] minimum
\item[-] minister
\item[-] minor
\item[-] minority
\item[-] minute
\item[-] mirror
\item[-] Miss
\item[-] miss
\item[-] missile
\item[-] missing
\item[-] mission
\item[-] mist
\item[-] mistake
\item[-] mix
\item[-] mixture
\item[-] mobile
\\mobile phone
\item[-] mode
\item[-] model
\item[-] modern
\item[-] moment
\item[-] Monday
\item[-] money
\item[-] monitor
\item[-] monkey
\item[-] month
\item[-] monthly
\item[-] mood
\item[-] moon
\item[-] moral
\item[-] more
\item[-] moreover
\item[-] morning
\item[-] mosquito
\item[-] most
\item[-] mostly
\item[-] mother (mum)
\item[-] motion
\item[-] motivate
\item[-] motive
\item[-] motor
\item[-] mount
\item[-] mountain
\item[-] mouse
\item[-] mouth
\item[-] move
\item[-] movement
\item[-] movie
\item[-] Mr
\item[-] Mrs
\item[-] Ms
\item[-] much
\item[-] mud
\item[-] multiple
\item[-] murder
\item[-] muscle
\item[-] museum
\item[-] mushroom
\item[-] must
\item[-] my
\item[-] myself
\item[-] maid
\item[-] marble
\item[-] mat
\item[-] meanwhile
\item[-] merchan
\item[-] modest
\item[-] modesty
\item[-] motto
\item[-] multiply
\item[-] mutton
\item[-] magnificent
\item[-] mall
\item[-] marine
\item[-] metaphor
\item[-] migration
\item[-] miracle
\item[-] modernization
\item[-] monument
\item[-] mutual
\item[-] mystery
\item[-] myth
\end{itemize}
\end{multicols}
\section{N}
\raggedcolumns
\begin{multicols}{2}
\begin{itemize}
\item[-] nail
\item[-] name
\item[-] narrow
\item[-] nation
\item[-] national
\item[-] nationality
\item[-] native
\item[-] natural
\item[-] nature
\item[-] navy
\item[-] near
\item[-] nearby
\item[-] nearly
\item[-] neat
\item[-] necessary
\item[-] neck
\item[-] need
\item[-] needle
\item[-] nagative
\item[-] negotiate
\item[-] neighbour (neighbor)
\item[-] neighbourhoof (neighborhood)
\item[-] neither
\item[-] nephew
\item[-] nervous
\item[-] nest
\item[-] net
\item[-] network
\item[-] never
\item[-] nevertheless
\item[-] new
\item[-] news
\item[-] newspaper
\item[-] next
\item[-] nice
\item[-] niece
\item[-] night
\item[-] nine
\item[-] nineteen
\item[-] ninety
\item[-] ninth
\item[-] no
\item[-] noble
\item[-] nobody
\item[-] nod
\item[-] noise
\item[-] noisy
\item[-] none
\item[-] noodle
\item[-] noon
\item[-] nor
\item[-] normal
\item[-] nose
\item[-] not
\item[-] note
\item[-] notebook
\item[-] nothing
\item[-] notice
\item[-] novel
\item[-] novelist
\item[-] November
\item[-] now
\item[-] nowadays
\item[-] nowhere
\item[-] nuclear
\item[-] number
\item[-] nurse
\item[-] nut
\item[-] nutrition
\item[-] numb
\item[-] nursery
\item[-] neutral
\item[-] numerous
\end{itemize}
\end{multicols}
\section{O}
\raggedcolumns
\begin{multicols}{2}
\begin{itemize}
\item[-] object
\item[-] objective
\item[-] observe
\item[-] obtain
\item[-] obviously
\item[-] occasion
\item[-] occupation
\item[-] occupy
\item[-] occur
\item[-] ocean
\item[-] o{\textquoteright}clock
\item[-] October
\item[-] odd
\item[-] of
\item[-] off
\item[-] offer
\item[-] office
\item[-] officer
\item[-] official
\item[-] often
\item[-] oil
\item[-] OK
\item[-] old
\item[-] Olympics
\\Olympic
\item[-] on
\item[-] once
\item[-] one
\item[-] onion
\item[-] online
\item[-] only
\item[-] onto
\item[-] open
\item[-] opera
\item[-] operation
\item[-] operator
\item[-] opinion
\item[-] opponent
\item[-] opportunity
\item[-] oppose
\item[-] opposite
\item[-] optimistic
\item[-] option
\item[-] or
\item[-] orange
\item[-] orbit
\item[-] order
\item[-] ordinary
\item[-] organ
\item[-] organic
\item[-] organisation (organization)
\item[-] origin
\item[-] original
\item[-] other
\item[-] otherwise
\item[-] ought to
\item[-] our
\item[-] ours
\item[-] ourselves
\item[-] out
\item[-] outcome
\item[-] outgoing
\item[-] outline
\item[-] output
\item[-] outside
\item[-] outstanding
\item[-] over
\item[-] overall
\item[-] overcome
\item[-] overseas
\item[-] owe
\item[-] own
\item[-] oxygen
\item[-] obey
\item[-] Oceania
\item[-] offend
\item[-] offshore
\item[-] oral
\item[-] outdoor
\item[-] outing
\item[-] outspoken
\item[-] outward(s)
\item[-] overhead
\item[-] overlook
\item[-] overweight
\item[-] ox (\emph{pl.} oxen)
\item[-] obstacle
\item[-] operate
\item[-] orchestra
\item[-] organise (organize)
\item[-] oven
\end{itemize}
\end{multicols}
\section{P}
\raggedcolumns
\begin{multicols}{2}
\begin{itemize}
\item[-] pace
\item[-] Pacific
\item[-] pack
\item[-] package
\item[-] page
\item[-] pain
\item[-] paint
\item[-] pair
\item[-] palace
\item[-] pale
\item[-] pan
\item[-] pancake
\item[-] panda
\item[-] panel
\item[-] panic
\item[-] paper
\item[-] paragragh
\item[-] parcel
\item[-] pardon
\item[-] parent
\item[-] park
\item[-] parking
\item[-] part
\item[-] participate
\item[-] particular
\item[-] partner
\item[-] party
\item[-] pass
\item[-] passage
\item[-] passenger
\item[-] passion
\item[-] passive
\item[-] passport
\item[-] past
\item[-] patent
\item[-] path
\item[-] patience
\item[-] patient
\item[-] pattern
\item[-] pay
\item[-] PE (physical education)
\item[-] peace
\item[-] peak
\item[-] pear
\item[-] pen
\item[-] pencil
\item[-] people
\item[-] pepper
\item[-] per
\item[-] perceive
\item[-] percent
\item[-] percentage
\item[-] perfect
\item[-] performance
\item[-] perhaps
\item[-] period
\item[-] permanent
\item[-] permit
\item[-] person
\item[-] personal
\item[-] personality
\item[-] persuade
\item[-] pessimistic
\item[-] pet
\item[-] petrol
\item[-] phase
\item[-] phenomenon
\item[-] philosophy
\item[-] phone
\item[-] photo (photograph)
\item[-] photographer
\item[-] phrase
\item[-] physician
\item[-] physics
\item[-] piano
\item[-] pick
\item[-] picnic
\item[-] picture
\item[-] pie
\item[-] piece
\item[-] pig
\item[-] pill
\item[-] pilot
\item[-] pink
\item[-] pioneer
\item[-] pipe
\item[-] pity
\item[-] place
\item[-] plain
\item[-] plan
\item[-] plane
\item[-] planet
\item[-] plant
\item[-] plastic
\item[-] plate
\item[-] platform
\item[-] play
\item[-] player
\item[-] playground
\item[-] pleasant
\item[-] please
\item[-] pleasure
\item[-] plenty
\item[-] plot
\item[-] plug
\item[-] plus
\item[-] p.m.
\item[-] pocket
\item[-] poem
\item[-] poet
\item[-] poetry
\item[-] point
\item[-] poison
\item[-] polar
\item[-] pole
\item[-] police
\item[-] policeman / policewoman
\item[-] policy
\item[-] polish
\item[-] polite
\item[-] political
\item[-] politician
\item[-] politics
\item[-] pollute
\item[-] pollution
\item[-] pond
\item[-] pool
\item[-] poor
\item[-] popular (pop)
\item[-] population
\item[-] pork
\item[-] port
\item[-] pose
\item[-] position
\item[-] positive
\item[-] possession
\item[-] possible
\item[-] post
\item[-] postcard
\item[-] poster
\item[-] postman
\item[-] postpone
\item[-] pot
\item[-] potato
\item[-] potential
\item[-] pound
\item[-] pour
\item[-] power
\item[-] practical
\item[-] practice
\item[-] praise
\item[-] pray
\item[-] precious
\item[-] precisely
\item[-] predict
\item[-] prefer
\item[-] preference
\item[-] prejudice
\item[-] premier
\item[-] prepare
\item[-] present
\item[-] presentation
\item[-] preserve
\item[-] president
\item[-] press
\item[-] pressure
\item[-] pretend
\item[-] pretty
\item[-] prevent
\item[-] previous
\item[-] price
\item[-] pride
\item[-] primary
\item[-] primitive
\item[-] principle
\item[-] print
\item[-] prior
\item[-] priority
\item[-] prison
\item[-] private
\item[-] prize
\item[-] probably
\item[-] problem
\item[-] procedure
\item[-] proceed
\item[-] process
\item[-] produce
\item[-] product
\item[-] profession
\item[-] professional
\item[-] professor
\item[-] profile
\item[-] profit
\item[-] programme (program)
\item[-] progress
\item[-] prohibit
\item[-] project
\item[-] promise
\item[-] promote
\item[-] pronounce
\item[-] pronunciation
\item[-] proof
\item[-] proper
\item[-] property
\item[-] proposal
\item[-] prospect
\item[-] protect
\item[-] protein
\item[-] protest
\item[-] proud
\item[-] prove
\item[-] provide
\item[-] province
\item[-] psychology
\item[-] pub
\item[-] public
\item[-] publish
\item[-] pudding
\item[-] pull
\item[-] punish
\item[-] pupil
\item[-] purchase
\item[-] pure
\item[-] purple
\item[-] purpose
\item[-] purse
\item[-] pursue
\item[-] push
\item[-] put
\item[-] pocket
\item[-] paddle
\item[-] parallel
\item[-] parrot
\item[-] part-time
\item[-] passer-by
\item[-] pause
\item[-] pavement
\item[-] pea
\item[-] peach
\item[-] pedestrian
\item[-] penny
\item[-] penniless
\item[-] pension
\item[-] perfume
\item[-] personnel
\item[-] pest
\item[-] pile
\item[-] pillow
\item[-] pin
\item[-] packet
\item[-] pagoda
\item[-] pants
\item[-] patriotism
\item[-] penguin
\item[-] perform
\item[-] perspective
\item[-] ping-pong
\item[-] pizza
\item[-] porridge
\item[-] protrait
\item[-] poverty
\item[-] prince / princess
\item[-] principal
\item[-] proportion
\item[-] prosperity
\item[-] puzzle
\item[-] pyramid
\end{itemize}
\end{multicols}
\section{Q}
\raggedcolumns
\begin{multicols}{2}
\begin{itemize}
\item[-] qualification
\item[-] qualify
\item[-] quality
\item[-] quarter
\item[-] queen
\item[-] question
\item[-] quick
\item[-] quiet
\item[-] quit
\item[-] quite
\item[-] quote
\item[-] quarrel
\item[-] questionnaire
\item[-] queue
\item[-] quilt
\item[-] quiz
\end{itemize}
\end{multicols}
\section{R}
\raggedcolumns
\begin{multicols}{2}
\begin{itemize}
\item[-] rabbit
\item[-] race
\item[-] racial
\item[-] radiation
\item[-] radio
\item[-] radium
\item[-] railway
\item[-] rain
\item[-] rainbow
\item[-] rainy
\item[-] raise
\item[-] random
\item[-] range
\item[-] rank
\item[-] rapid
\item[-] rare
\item[-] rate
\item[-] rather
\item[-] rating
\item[-] raw
\item[-] ray
\item[-] reach
\item[-] react
\item[-] reaction
\item[-] read
\item[-] ready
\item[-] real
\item[-] realise (realize)
\item[-] realistic
\item[-] reality
\item[-] really
\item[-] reason
\item[-] recall
\item[-] receipt
\item[-] receive
\item[-] recently
\item[-] receptionist
\item[-] recipe
\item[-] recite
\item[-] recognise (recognize)
\item[-] recognition
\item[-] recommend
\item[-] record
\item[-] recording
\item[-] recover
\item[-] recreation
\item[-] recycle
\item[-] red
\item[-] reduce
\item[-] refer
\item[-] reference
\item[-] reflect
\item[-] reform
\item[-] refresh
\item[-] refuse
\item[-] regard
\item[-] regardless
\item[-] region
\item[-] register
\item[-] regret
\item[-] regular
\item[-] reject
\item[-] relate
\item[-] relationship
\item[-] relative
\item[-] relax
\item[-] relay
\item[-] release
\item[-] relevant
\item[-] reliable
\item[-] relief
\item[-] rely
\item[-] remain
\item[-] remarkable
\item[-] remember
\item[-] remind
\item[-] remote
\item[-] remove
\item[-] rent
\item[-] repair
\item[-] repeat
\item[-] replace
\item[-] reply
\item[-] report
\item[-] represent
\item[-] representative
\item[-] republic
\item[-] reputation
\item[-] request
\item[-] require
\item[-] rescue
\item[-] research
\item[-] reserve
\item[-] resident
\item[-] resign
\item[-] resistance
\item[-] resolution
\item[-] resolve
\item[-] resource
\item[-] respect
\item[-] respective
\item[-] respond
\item[-] response
\item[-] responsibility
\item[-] resonsible
\item[-] rest
\item[-] restaurant
\item[-] restore
\item[-] restrict
\item[-] result
\item[-] retire
\item[-] return
\item[-] reveal
\item[-] review
\item[-] revise
\item[-] reward
\item[-] rhyme
\item[-] rice
\item[-] rich
\item[-] riddle
\item[-] ride
\item[-] right
\item[-] rigid
\item[-] ring
\item[-] ripe
\item[-] rise
\item[-] risk
\item[-] river
\item[-] road
\item[-] roast
\item[-] robot
\item[-] rock
\item[-] rocket
\item[-] role
\item[-] roll
\item[-] romantic
\item[-] roof
\item[-] room
\item[-] root
\item[-] rope
\item[-] rose
\item[-] round
\item[-] route
\item[-] routine
\item[-] row
\item[-] royal
\item[-] rubber
\item[-] rubbish
\item[-] rude
\item[-] rugby
\item[-] ruin
\item[-] rule
\item[-] ruler
\item[-] run
\item[-] rural
\item[-] rush
\item[-] Russia
\item[-] Russian
\item[-] radioactive
\item[-] rag
\item[-] rail
\item[-] rainfall
\item[-] razor
\item[-] rectangle
\item[-] regulation
\item[-] referee
\item[-] refrigerator
\item[-] religion
\item[-] remark
\item[-] repeat
\item[-] recent
\item[-] reinforce
\item[-] rejuvenate
\item[-] relieve
\item[-] revolution
\item[-] rival
\item[-] rough
\end{itemize}
\end{multicols}
\section{S}
\raggedcolumns
\begin{multicols}{2}
\begin{itemize}
\item[-] sad
\item[-] safe
\item[-] safety
\item[-] sail
\item[-] salad
\item[-] salary
\item[-] sale
\item[-] salesman / saleswoman
\item[-] salt
\item[-] salty
\item[-] same
\item[-] sample
\item[-] sand
\item[-] sandwich
\item[-] satellite
\item[-] satisfaction
\item[-] satisfy
\item[-] Saturday
\item[-] saucer
\item[-] sausage
\item[-] save
\item[-] saving
\item[-] say
\item[-] saying
\item[-] scare
\item[-] scarf
\item[-] scene
\item[-] schedule
\item[-] scholarship
\item[-] school
\item[-] schoolbag
\item[-] science
\item[-] scientific
\item[-] scientist
\item[-] scissors
\item[-] score
\item[-] scream
\item[-] screen
\item[-] sculpture
\item[-] sea
\item[-] search
\item[-] season
\item[-] seat
\item[-] second
\item[-] secondary
\item[-] secret
\item[-] secretary
\item[-] section
\item[-] secure
\item[-] security
\item[-] see
\item[-] seed
\item[-] seek
\item[-] seem
\item[-] seize
\item[-] seldom
\item[-] select
\item[-] sell
\item[-] send
\item[-] senior
\item[-] sense
\item[-] sensitive
\item[-] sentence
\item[-] separate
\item[-] September
\item[-] series
\item[-] serious
\item[-] servant
\item[-] serve
\item[-] service
\item[-] session
\item[-] set
\item[-] setting
\item[-] settle
\item[-] seven
\item[-] seventeen
\item[-] seventh
\item[-] seventy
\item[-] several
\item[-] severe
\item[-] sew
\item[-] sex
\item[-] shade
\item[-] shadow
\item[-] shake
\item[-] shall
\item[-] shallow
\item[-] shame
\item[-] shape
\item[-] share
\item[-] shark
\item[-] sharp
\item[-] shave
\item[-] she
\item[-] sheep
\item[-] sheet
\item[-] shelf
\item[-] shelter
\item[-] shift
\item[-] shine
\item[-] ship
\item[-] shirt
\item[-] shock
\item[-] shoe
\item[-] shoot
\item[-] shop
\item[-] shore
\item[-] short
\item[-] shortage
\item[-] shorts
\item[-] should
\item[-] shoulder
\item[-] shout
\item[-] show
\item[-] shower
\item[-] shut
\item[-] shy
\item[-] sick
\item[-] side
\item[-] sight
\item[-] sign
\item[-] signal
\item[-] significant
\item[-] silence
\item[-] silent
\item[-] silk
\item[-] silly
\item[-] silver
\item[-] similar
\item[-] simple
\item[-] since
\item[-] sincerely
\item[-] sing
\item[-] single
\item[-] sink
\item[-] sir
\item[-] sister
\item[-] sit
\item[-] site
\item[-] situation
\item[-] six
\item[-] sixteen
\item[-] sixth
\item[-] sixty
\item[-] size
\item[-] skate
\item[-] skateboard
\item[-] ski
\item[-] skill
\item[-] skin
\item[-] skip
\item[-] skirt
\item[-] sky
\item[-] sleep
\item[-] sleepy
\item[-] slice
\item[-] slide
\item[-] slightly
\item[-] slim
\item[-] slip
\item[-] slow
\item[-] small
\item[-] smart
\item[-] smell
\item[-] smile
\item[-] smog
\item[-] smoke
\item[-] smooth
\item[-] snack
\item[-] snake
\item[-] sneeze
\item[-] snow
\item[-] snowy
\item[-] so
\item[-] soccer
\item[-] social
\item[-] socialist
\item[-] society
\item[-] sock
\item[-] sofa
\item[-] soft
\item[-] software
\item[-] soil
\item[-] solar
\item[-] soldier
\item[-] solid
\item[-] solution
\item[-] solve
\item[-] some
\item[-] somebody
\item[-] somehow
\item[-] someone
\item[-] something
\item[-] sometimes
\item[-] somewhat
\item[-] somewhere
\item[-] son
\item[-] song
\item[-] soon
\item[-] sorrow
\item[-] sorry
\item[-] sort
\item[-] soul
\item[-] sound
\item[-] soup
\item[-] sour
\item[-] source
\item[-] south
\item[-] southern
\item[-] sow
\item[-] space
\item[-] spare
\item[-] speak
\item[-] speaker
\item[-] special
\item[-] specialist
\item[-] species
\item[-] specific
\item[-] speech
\item[-] speed
\item[-] spell
\item[-] spend
\item[-] spirit
\item[-] splendid
\item[-] sponsor
\item[-] spoon
\item[-] sport
\item[-] spot
\item[-] spread
\item[-] spring
\item[-] spy
\item[-] square
\item[-] stability
\item[-] stadium
\item[-] staff
\item[-] stage
\item[-] stair
\item[-] stamp
\item[-] stand
\item[-] standard
\item[-] star
\item[-] stare
\item[-] start
\item[-] starve
\item[-] state
\item[-] station
\item[-] statistic
\item[-] statue
\item[-] stay
\item[-] steak
\item[-] steal
\item[-] steam
\item[-] steel
\item[-] step
\item[-] stick
\item[-] still
\item[-] stimulate
\item[-] stomach
\item[-] stomachache
\item[-] stone
\item[-] stop
\item[-] store
\item[-] storm
\item[-] story
\item[-] straight
\item[-] straightforward
\item[-] strait
\item[-] strange
\item[-] stranger
\item[-] strategy
\item[-] strawberry
\item[-] stream
\item[-] street
\item[-] strength
\item[-] strengthen
\item[-] stress
\item[-] stretch
\item[-] strict
\item[-] strike
\item[-] string
\item[-] structure
\item[-] struggle
\item[-] student
\item[-] studio
\item[-] study
\item[-] stuff
\item[-] stupid
\item[-] style
\item[-] subject
\item[-] subjective
\item[-] submit
\item[-] subscribe
\item[-] subsequent
\item[-] substance
\item[-] substantial
\item[-] suburb
\item[-] subway
\item[-] succeed
\item[-] success
\item[-] successful
\item[-] such
\item[-] sudden
\item[-] suffer
\item[-] sufficient
\item[-] sugar
\item[-] suggest
\item[-] suggestion
\item[-] suit
\item[-] suitable
\item[-] sum
\item[-] summary
\item[-] summer
\item[-] sun
\item[-] Sunday
\item[-] sunny
\item[-] super
\item[-] superb
\item[-] superior
\item[-] supermarket
\item[-] supply
\item[-] support
\item[-] suppose
\item[-] sure
\item[-] surf
\item[-] surface
\item[-] surgeon
\item[-] surgery
\item[-] surprise
\item[-] surround
\item[-] surrounding
\item[-] survey
\item[-] survive
\item[-] suspect
\item[-] suspend
\item[-] sustain
\item[-] sweat
\item[-] sweater
\item[-] sweep
\item[-] sweet
\item[-] swim
\item[-] swimming
\item[-] swing
\item[-] switch
\item[-] symbol
\item[-] sympathy
\item[-] symphony
\item[-] system
\item[-] sacred
\item[-] sacrifice
\item[-] salute
\item[-] scan
\item[-] skeptical
\item[-] scholar
\item[-] scholarship
\item[-] scratch
\item[-] seagull
\item[-] seal
\item[-] seaweed
\item[-] selfish
\item[-] semicircle
\item[-] shortcoming
\item[-] shrink
\item[-] shuttle
\item[-] sigh
\item[-] skyscraper
\item[-] slave
\item[-] slavery
\item[-] sleeve
\item[-] sniff
\item[-] sob
\item[-] spade
\item[-] sparrow
\item[-] spin
\item[-] spit
\item[-] spray
\item[-] squeeze
\item[-] squirrel
\item[-] stain
\item[-] status
\item[-] steady
\item[-] stout
\item[-] stove
\item[-] straw
\item[-] stubborn
\item[-] substitude
\item[-] suitcase
\item[-] sunburnt
\item[-] supreme
\item[-] surplus
\item[-] swallow
\item[-] swap
\item[-] swear
\item[-] swell
\item[-] swift
\item[-] sword
\item[-] symptom
\item[-] sauce
\item[-] scale
\item[-] semester
\item[-] shell
\item[-] socialism
\item[-] sore
\item[-] souvenir
\item[-] spacecraft
\item[-] spicy
\item[-] split
\item[-] supplement
\end{itemize}
\end{multicols}
\section{T}
\raggedcolumns
\begin{multicols}{2}
\begin{itemize}
\item[-] table
\item[-] tablet
\item[-] tackle
\item[-] tail
\item[-] tailor
\item[-] take
\item[-] tale
\item[-] talent
\item[-] talk
\item[-] tall
\item[-] tank
\item[-] tape
\item[-] target
\item[-] task
\item[-] taste
\item[-] tax
\item[-] taxi
\item[-] tea
\item[-] teach
\item[-] teacher
\item[-] team
\item[-] teapot
\item[-] tear
\item[-] technique
\item[-] technology
\item[-] teenager
\item[-] telephone
\item[-] telescope
\item[-] television (TV)
\item[-] tell
\item[-] temperature
\item[-] temple
\item[-] temporary
\item[-] ten
\item[-] tend
\item[-] tendency
\item[-] tennis
\item[-] tension
\item[-] tenth
\item[-] term
\item[-] terrible
\item[-] territory
\item[-] test
\item[-] text
\item[-] than
\item[-] thank
\item[-] that
\item[-] the
\item[-] theatre
\item[-] theft
\item[-] their
\item[-] them
\item[-] theme
\item[-] themselves
\item[-] then
\item[-] theory
\item[-] there
\item[-] therefore
\item[-] these
\item[-] they
\item[-] thick
\item[-] thin
\item[-] thing
\item[-] think
\item[-] thinking
\item[-] third
\item[-] thirsty
\item[-] this
\item[-] thorough
\item[-] those
\item[-] though
\item[-] thought
\item[-] thousand
\item[-] threat
\item[-] threaten
\item[-] three
\item[-] through
\item[-] throughout
\item[-] throw
\item[-] thunder
\item[-] Thursday
\item[-] thus
\item[-] ticket
\item[-] tidy
\item[-] tie
\item[-] tiger
\item[-] tight
\item[-] time
\item[-] tiny
\item[-] tip
\item[-] tired
\item[-] tissue
\item[-] title
\item[-] to
\item[-] toast
\item[-] tobacco
\item[-] today
\item[-] together
\item[-] toilet
\item[-] tolerate
\item[-] tomato
\item[-] tomorrow
\item[-] ton
\item[-] tone
\item[-] tonight
\item[-] too
\item[-] tool
\item[-] tooth (\emph{pl.} teeth)
\item[-] toothache
\item[-] top
\item[-] topic
\item[-] total
\item[-] touch
\item[-] tour
\item[-] tourist
\item[-] tournament
\item[-] toward(s)
\item[-] towel
\item[-] tower
\item[-] town
\item[-] toy
\item[-] track
\item[-] trade
\item[-] tradition
\item[-] traditional
\item[-] tracffic
\item[-] train
\item[-] training
\item[-] transform
\item[-] translate
\item[-] transport
\item[-] trap
\item[-] travel
\item[-] treasure
\item[-] treat
\item[-] treatment
\item[-] tree
\item[-] trend
\item[-] trial
\item[-] trick
\item[-] trip
\item[-] trouble
\item[-] trousers
\item[-] truck
\item[-] true
\item[-] trunk
\item[-] trust
\item[-] truth
\item[-] try
\item[-] T-shirt
\item[-] tube
\item[-] Tuesday
\item[-] tune
\item[-] turkey
\item[-] turn
\item[-] twelfth
\item[-] twelve
\item[-] twentieth
\item[-] twenty
\item[-] twice
\item[-] twin
\item[-] two
\item[-] type
\item[-] typhoon
\item[-] typical
\item[-] tap
\item[-] tease
\item[-] tentative
\item[-] terminal
\item[-] terrify
\item[-] thermos
\item[-] thief
\item[-] thread
\item[-] thrill
\item[-] thriller
\item[-] throat
\item[-] tick
\item[-] timetable
\item[-] tiresome
\item[-] tomb
\item[-] tongue
\item[-] transparent
\item[-] tremble
\item[-] triangle
\item[-] trolleybus
\item[-] troop
\item[-] troublesome
\item[-] twist
\item[-] teamwork
\item[-] teenage
\item[-] tent
\item[-] theirs
\item[-] transfer
\item[-] transition
\item[-] tropical
\item[-] tunnel
\end{itemize}
\end{multicols}
\section{U}
\raggedcolumns
\begin{multicols}{2}
\begin{itemize}
\item[-] ugly
\item[-] UK
\item[-] ultimately
\item[-] umbrella
\item[-] uncle
\item[-] under
\item[-] underground
\item[-] understand
\item[-] uniform
\item[-] unique
\item[-] unit
\item[-] universe
\item[-] university
\item[-] unless
\item[-] until (till)
\item[-] unusual
\item[-] up
\item[-] update
\item[-] upon
\item[-] upper
\item[-] upset
\item[-] urban
\item[-] urge
\item[-] urgent
\item[-] us
\item[-] use
\item[-] used
\item[-] useful
\item[-] usual
\item[-] usaully
\item[-] unbearable
\item[-] unbelievable
\item[-] uncertain
\item[-] unconditional
\item[-] unconscious
\item[-] underline
\item[-] undertake
\item[-] underwear
\item[-] unfair
\item[-] unfit
\item[-] unfortunate
\item[-] unemployment
\item[-] union
\end{itemize}
\end{multicols}
\section{V}
\raggedcolumns
\begin{multicols}{2}
\begin{itemize}
\item[-] vacation
\item[-] valley
\item[-] valuable
\item[-] value
\item[-] variation
\item[-] variety
\item[-] various
\item[-] vary
\item[-] vase
\item[-] vast
\item[-] vegetable
\item[-] vehicle
\item[-] venue
\item[-] version
\item[-] very
\item[-] victim
\item[-] victory
\item[-] video
\item[-] view
\item[-] village
\item[-] violence
\item[-] violin
\item[-] virtual
\item[-] virtue
\item[-] virus
\item[-] visible
\item[-] vision
\item[-] visit
\item[-] visitor
\item[-] visual
\item[-] vital
\item[-] vivid
\item[-] vocabulary
\item[-] voice
\item[-] volcano
\item[-] volleyball
\item[-] volume
\item[-] volunteer
\item[-] vote
\item[-] vacant
\item[-] vague
\item[-] vain
\item[-] valid
\item[-] vertical
\item[-] violate
\item[-] voluntary
\item[-] voyage
\end{itemize}
\end{multicols}
\section{W}
\raggedcolumns
\begin{multicols}{2}
\begin{itemize}
\item[-] wage
\item[-] waist
\item[-] wait
\item[-] wake
\item[-] walk
\item[-] wall
\item[-] wallet
\item[-] wander
\item[-] want
\item[-] war
\item[-] ward
\item[-] warm
\item[-] warn
\item[-] warning
\item[-] wash
\item[-] washroom
\item[-] waste
\item[-] watch
\item[-] water
\item[-] watermelon
\item[-] wave
\item[-] way
\item[-] we
\item[-] weak
\item[-] wealth
\item[-] weapon
\item[-] wear
\item[-] weather
\item[-] website
\item[-] wedding
\item[-] Wednesday
\item[-] weed
\item[-] week
\item[-] weekday
\item[-] weekend
\item[-] weekly
\item[-] weep
\item[-] weigh
\item[-] weight
\item[-] welcome
\item[-] welfare
\item[-] well
\item[-] west
\item[-] western
\item[-] wet
\item[-] whale
\item[-] what
\item[-] whatever
\item[-] wheat
\item[-] wheel
\item[-] when
\item[-] whenever
\item[-] where
\item[-] whether
\item[-] which
\item[-] while
\item[-] whisper
\item[-] white
\item[-] who
\item[-] whole
\item[-] whom
\item[-] whose
\item[-] why
\item[-] wide
\item[-] widespread
\item[-] wife
\item[-] Wi-Fi
\item[-] wild
\item[-] will
\item[-] win
\item[-] wind
\item[-] window
\item[-] windy
\item[-] wine
\item[-] wing
\item[-] winner
\item[-] winter
\item[-] wire
\item[-] wisdom
\item[-] wise
\item[-] wish
\item[-] with
\item[-] withdraw
\item[-] within
\item[-] without
\item[-] witness
\item[-] woman
\item[-] wonder
\item[-] wonderful
\item[-] wood
\item[-] wool
\item[-] word
\item[-] work
\item[-] worker
\item[-] world
\item[-] worry
\item[-] worse
\item[-] worst
\item[-] worth
\item[-] worthwhile
\item[-] worthy
\item[-] would
\item[-] wound
\item[-] wrap
\item[-] wrestle
\item[-] wrinkle
\item[-] wrist
\item[-] write
\item[-] writer
\item[-] wrong
\item[-] wag
\item[-] walnut
\item[-] warehouse
\item[-] wax
\item[-] whistle
\item[-] willing
\item[-] worm
\item[-] web
\item[-] wetland
\item[-] wolf
\end{itemize}
\end{multicols}
\section{X}
\raggedcolumns
\begin{multicols}{2}
\begin{itemize}
\item[-] X-ray
\end{itemize}
\end{multicols}
\section{Y}
\raggedcolumns
\begin{multicols}{2}
\begin{itemize}
\item[-] yard
\item[-] year
\item[-] yellow
\item[-] yes
\item[-] yesterday
\item[-] yet
\item[-] yoghurt
\item[-] you
\item[-] young
\item[-] your
\item[-] yours
\item[-] yourself
\item[-] youth
\item[-] yawn
\item[-] yell
\item[-] yummy
\item[-] yield
\end{itemize}
\end{multicols}
\section{Z}
\raggedcolumns
\begin{multicols}{2}
\begin{itemize}
\item[-] zero
\item[-] zone
\item[-] zoo
\item[-] zebra
\item[-] zipper
\item[-] zip
\item[-] zoom
\end{itemize}
\end{multicols}